---
title: 'Homework 4'
output:
  pdf_document: default
  html_document: default
date: "2023-04-18"
author: 'Brandon Hosley'
---
---
title: "Homework 4"
footer: 'HW 4'
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

```{r setup, include=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(xtable)
library(MASS)
library(readxl)
options(xtable.comment = FALSE, xtable.type="latex")
options(rgl.useNULL=TRUE)
#.rs.restartR()
library(qpcR)
library(kableExtra)
```

## Problem 1.

*Analyze the relationship between total team wins (y) and a set of regressors consisting of passing yards (x_2), turnover differential (x_5), and percent rushing plays (x_7)*

```{r, echo=TRUE}
df <- read_excel('../Homework 1/1989 NFL Season Data (Handout).xlsx', range = cell_rows(1:29))
```

### (a)

*Create a multiple regression model and perform a thorough influence analysis. Provide a table containing the predicted values, R-Student residuals, hat values, Cook’s D values, DFBETA values, DFFITS values, and COVRATIO values.*

```{r, echo=TRUE}
mod <- lm(y ~ x2 + x5 + x7, df)
p <- length(coef(mod))
table = data.frame('obs' = df$Team,
                   'y_hat' = mod[['fitted.values']],
                   't_i' = rstudent(mod),
                   'h_ii' = hatvalues(mod),
                   'D_i' = cooks.distance(mod),
                   'DFBETAS_int' = dfbetas(mod)[,'(Intercept)'],
                   'DFBETAS_x2' = dfbetas(mod)[,'x2'],
                   'DFBETAS_x5' = dfbetas(mod)[,'x5'],
                   'DFBETAS_x7' = dfbetas(mod)[,'x7'],
                   'DFFITS' = dffits(mod),
                   'COVRATIO' = covratio(mod))

names(table) <- c('Team','$\\hat{y}$','$t_i$','$h_{ii}$','$D_i$', '$DFBETAS$',
                  '$DFBETAS$','$DFBETAS$','$DFBETAS$','$DFFITS_i$','$COVRATIO_i$')

landscape(kable(table, escape = FALSE, booktabs = TRUE, digits = 3) 
          %>% add_header_above(c(" " = 5,
                                 "Intercept" = 1,
                                 "Passing Yards" = 1,
                                 "Turnover Differential" = 1,
                                 "Rush Percentage" = 1, ' ' = 2 )) 
          %>% kable_styling(latex_options = "scale_down"))
```



### (b)

*Give the thresholds for determining whether an observation is influential according to each metric.*

```{r, echo=T}
n <- length(df$Index)
h_ii <- 2*p/n
dfbet <- 2/sqrt(n)
dffit <- 2*sqrt(p/n)
cov_low <- 1 - 3*p/n
cov_high <- 1 + 3*p/n
```

$h_{ii} > \frac{2p}{n} = `r h_ii[1]`$  

$D_i > 1$

$|\text{DFBETAS}_{j,i}| > \frac{2}{\sqrt{n}} = `r dfbet`$

$|\text{DFFITS}_{i}| > 2\sqrt{\frac{p}{n}} = `r dffit`$

$`r cov_low` = 1-\frac{3p}{n} < \text{COVRATIO} < 1+\frac{3p}{n} = `r cov_high`$

### (c)

*Identify and discuss which observations are influential according to which influence measure.*

## Influence of $h_{ii}$
```{r, echo=T}
kable(table[c(abs(table$`$h_{ii}$`)>h_ii),c('Team','$h_{ii}$')], 
      escape = FALSE, booktabs = TRUE, digits = 3)
```

## Influence of $D_{i}$

```{r, echo=T}
kable(table[c(abs(table$`$D_i$`)>1),c('Team','$D_i$')], escape = FALSE, booktabs = TRUE, digits = 3)
```

## Influence of DFBETAS

```{r, echo=T}
kable(table[c(abs(table[6]) > dfbet | 
              abs(table[7]) > dfbet | 
              abs(table[8]) > dfbet | 
              abs(table[9]) > dfbet), c(1,6,7,8,9)], escape = FALSE, booktabs = TRUE, digits = 3)
```

## Influence of DFFITS

```{r, echo=T}
kable(table[c(abs(table$`$DFFITS_i$`)>dffit), c('Team','$DFFITS_i$')], escape = FALSE, booktabs = TRUE, digits = 3)
```

## Influence of COVRATIO

```{r, echo=T}
kable(table[c(table$`$COVRATIO_i$` > cov_high | table$`$COVRATIO_i$` < cov_low), c('Team','$COVRATIO_i$')], escape = FALSE, booktabs = TRUE, digits = 3)
```

From these results we can see that several teams meet the influential thresholds for most of the features, except $D_i$. The Seahawks and Falcons both occur in these results in multiple instances. What this suggests is that these teams are highly influential on the regression as a whole. In the case of the Falcons' underperformance and the Seahawks' overperformance is exceptional relative to several of the measurements listed above.
