---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 8 Practical Exercise"
footer: `r paste('Lesson 8 Practical Exercise')`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(printr)
library(xtable)
library(formatR)
library(nlme)
options(xtable.comment = FALSE, xtable.type="latex")
```

# Perform data housekeeping - upload data for Example 5.6, Example 5.7, and Printing Ink; name columns, display to make sure it reads properly, etc. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df6 <- read.xlsx('./data-ex-5-6.xlsx', sheetIndex = 1)
df7 <- read.xlsx('./data-ex-5-7.xlsx', sheetIndex = 1)
names(df7) <- c('observation', 'time', 'cases', 'distance', 'city')
dfI <- read.xlsx('./data-ex-PrintingInk.xlsx', sheetIndex = 1)
```

# 2. Example 5.5 Method (using Printing Ink data) 

## a) Create a linear model relating the regressors to the standard deviation ('s' in th data file)

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
I_reg_s_mod <- lm(dfI$s ~ dfI$x1 + dfI$x2 + dfI$x3)
summary(I_reg_s_mod)
```

## b) Define model weights

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
dfI['w'] <- 1/ sqrt(abs(residuals(I_reg_s_mod)))
#dfI['w'] <- 1 / dfI$s**2
#dfI$w <- replace(dfI$w, dfI$w>1, 0)
#interp <- mean(dfI$w)
#dfI$w <- replace(dfI$w, dfI$w==0, interp)
```

Our weights are estimated using the inverse of each entry's variance
Since division by zero would otherwise happen, resulting in infinite weight, those are replace with average.

## c) Solve weighted least squares using matrices

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
library(MASS)
N <- dim(dfI)[1]
X <- matrix(c(rep(1, N), dfI$x1, dfI$x2, dfI$x3), ncol = 4, byrow = FALSE)
B <- X * c(sqrt(dfI$w))
z <- matrix(dfI$y_bar) * c(sqrt(dfI$w))
beta <- ginv(t(B) %*% B) %*% t(B) %*% z
print(beta)
```

## d) Solve weighted least squares using lm() and entering weights


```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
I_reg_mod <- lm(dfI$y_bar ~ dfI$x1 + dfI$x2 + dfI$x3)
summary(I_reg_mod)
```

## e) Display both sets of coefficients - should be the same (minor differences possible due to rounding)

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
t(beta)
coef(I_reg_mod)
```

These values are hand grenade close rather than horseshoe close.

# 3. Example 5.6 (p. 196-199)

## a) Create a linear model predicting time as a function of aspect, paper,and the interaction. Results should match Table 5.11.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_6 <- lm(df6$Time ~ df6$Aspect + df6$Paper + df6$Interaction)
summary(mod_6)
```

## b) Create a linear model of groups, with the response being the group average (i.e. use Table 5.14 as input data). Results should match Table 5.15.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df6_avg <- df6
df6_avg$Time <- NULL
df6_avg <- unique(df6_avg)
df6_avg$Time <- tapply(df6$Time, df6$Helicopter, mean)
df6_avg
```

# 4. Example 5.7 (p.201-202)

## a) Run regression model using City as a random factor using lme(). Compare StdDev for (Intercept) and Residual to variances in Figure 5.12.


```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_7 <- lme(time ~ cases + distance, random = ~ 1|city, data = df7)

summary(mod_7)
```
