---
output:
  pdf_document: default
---
---
title: "Lesson 13 Practical Exercise"
footer: `r paste('Lesson 13 Practical Exercise')`
date: "`r format(as.Date(c('2021/05/10')), '%d %B %Y')`"
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript('../R/scripts/js/jquery.min.js')
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(printr)
library(xtable)
library(formatR)
library(ridge)
library(pls)
library(MASS)
library(car)
library(broom)
library(dplyr)
library(kableExtra)
options(xtable.comment = FALSE, xtable.type="latex")
```

```{r, include=FALSE}
kable <- function(data, ...) {
  knitr::kable(data, ..., 'latex', booktabs = TRUE, digits = 5, align = 'c') %>% 
    kable_styling( latex_options =c("hold_position"))
}
```

# Perform data housekeeping - upload data for Example 9.1; name columns, display to make sure it reads properly, etc. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df_9.1 <- read.xlsx('./data-ex-9-1.xlsx', sheetIndex = 1, colIndex = c(2,3,4,5))
names(df_9.1) <- c('C7H16_to_C2H2', 'Reactor_Temp', 'H2_to_C7H16', 'Contact_Time')
```

# 2. Example 9.1 (p. 290-292)
## a) Create scatterplot of ContactTime versuse ReactorTemperature.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(df_9.1[c('Reactor_Temp', 'Contact_Time')])
```

## b) Scale regressor variables using unit normal scaling.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df_9.1_scaled <- df_9.1
df_9.1_scaled[c('Reactor_Temp', 'H2_to_C7H16', 'Contact_Time')] <- 
  data.frame( scale( df_9.1[c('Reactor_Temp', 'H2_to_C7H16', 'Contact_Time')] ) )
```

## c) Fit second order model using scaled regressors, to include two-way interaction terms. Compare to Table 9.2 on p. 293.

Note: Can do this model the "long way", i.e. lm(y ~ x1 + x2 + x3 + x1x2 + x2x3... etc.) or using polym() function in R.
Model output for the polym() shortcut uses a particular notation. Don't get confused - know what you're looking at.
Model both ways and use each model to decipher the polum() output.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
pmod_9.1 <- lm(C7H16_to_C2H2~ polym(Reactor_Temp, H2_to_C7H16, Contact_Time, degree = 2, raw = TRUE), 
               data=df_9.1_scaled )
landscape(kable(xtable(summary(pmod_9.1), floating = F, scalebox = 0.5, justify = "center")))
```

I would appear that the price paid for the easier scripting with the poly() function is paid in the unfriendly output notation.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
names(pmod_9.1$coefficients) <- c('Intercept','$T$','$T^2$','$H$','$TH$','$H^2$','$C$','$TC$','$HC$','$C^2$')
kable(tidy(pmod_9.1), col.names = c('Term','Regression Coefficient', 'Standard Error', '$t_0$', '$p$ value') )
```

This matches the reference table.

## d) Reproduce Table 9.3 on p. 295.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}


standardized <- sweep(scale(df_9.1, scale=FALSE), 2, sqrt(diag(var(df_9.1))*(nrow(df_9.1)-1)), '/' ) #Stand
tbl_9.3 <- data.frame(standardized)
names(tbl_9.3) <- c('$y$','$x_1$','$x_2$','$x_3$')

poly_exp <- data.frame(c( tbl_9.3['$x_1$']*tbl_9.3['$x_2$'], tbl_9.3['$x_1$']*tbl_9.3['$x_3$'],
                          tbl_9.3['$x_2$']*tbl_9.3['$x_3$'], tbl_9.3['$x_1$']*tbl_9.3['$x_1$'],
                          tbl_9.3['$x_2$']*tbl_9.3['$x_2$'], tbl_9.3['$x_3$']*tbl_9.3['$x_3$']))

tbl_9.3[c('$x_1x_2$', '$x_1x_3$', '$x_2x_3$','$x_1^2$','$x_2^2$','$x_3^2$')] <-
  sweep(scale(poly_exp, scale=FALSE), 2, sqrt(diag(var(poly_exp))*(nrow(df_9.1)-1)), '/' )

kable(tbl_9.3) %>% kable_styling(latex_options = c("hold_position","scale_down"))
```

## e) Using Table 9.3 data, define an X matrix and perform eigensystem analysis of X'X. Compare to Table 9.10 on p. 316.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
X <- as.matrix( cbind(1, subset(tbl_9.3, select = -`$y$`)) )
e = eigen(t(X)%*%X)
eigvals = e$values[-1]
eigvecs = e$vectors[-1,-1]
kable(as.data.frame(cbind(eigvecs,eigvals)), col.names = NULL) %>% 
  add_header_above(c(' ' = 3, 'Eigenvectors' = 3, ' ' = 3, 'Eigenvalues  $\\lambda_j$')) %>% 
  kable_styling(latex_options = c("hold_position","scale_down"))
```

## f) Calculate kappa values and compare to p. 298.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
max(eigvals)/eigvals
```

# 3. Example 9.2 (p.307-308)

## a) Perform ridge regression (by hand) using the standardized data from Table 9.3. Devine the parameter k as a constant and vary to reproduce Table 9.8 on p. 308.

Note: The textbook leaves off the intercept term. This is because the response and the regressors are both centered and scaled. Due to rounding, the output will give a small B_0 coefficient. We could also drop the vector of ones from X

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
Xty <- t(X) %*% tbl_9.3$`$y$`
XtX <- t(X) %*% X
k <- 0.032
I <- diag(x = 1, nrow = length(XtX[, 1]))
Beta_ridge <- ginv(XtX + k * I) %*% Xty
Beta_ridge
```

## b) There is also a package to perform ridge regression automatically.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
linearRidge(tbl_9.3$`$y$` ~. ,subset(tbl_9.3, select = -`$y$`), lambda = 0.032)
```

# 4. Example 9.3 (p.316-319)

## a) Perform Principal Component Regression using the pcr() function. Display $coefficients, $loadings, and $scores. Compare to Table 9.12 on p. 318 and Table 9.10 on p. 3.16.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
ex9.3pcr <- pcr( tbl_9.3$`$y$` ~. ,data =subset(tbl_9.3, select = -`$y$`) )
summary(ex9.3pcr)
kable(as.data.frame(ex9.3pcr$coefficients)) %>% 
  kable_styling(latex_options = c("hold_position","scale_down"))
kable(cbind(ex9.3pcr$loadings))
kable(cbind(ex9.3pcr$scores))
```

## b) Perform Principal Component Regression (by hand) using the following steps:
### 1) Define matrix of eigenvectors of xTx, where X is defined by standardized variables (Table 9.3).

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
kable(eigvecs)
```

### 2) Calculate Z; omit intercept row/column because variables are standardized. Compare to $scores output from pcr().

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
Z <- X[,-1] %*% eigvecs
kable(Z)
```

### 3) Obtain least squares estimators for $\alpha$.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
alphas <- ginv(t(Z) %*% Z) %*% (t(Z) %*% tbl_9.3$`$y$`)
kable(t(alphas))
```

### 4) Define vector of ones and zeros to determine cutoff of principal components to use.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
B <- c(1,1,1,1,1,0,0,0,0)
```

### 5) Define $\alpha_{pc}$ as per p.315 (equation not numbered). Note that this is term-by-term multiplication, not the dot product.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
alpha_pc <- alphas * B
```

### 6) Calculate $\beta_{pc}$ using Equation 9.10. Compare results to Table 9.12 on p. 318. Vary B vector to obtain standardized estimates in columns A, B, C, D, and E.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
beta_pc <- eigvecs %*% alpha_pc # Equation 9.10. Compare results to Table 9.12 on p. 318.
kable(beta_pc)
```