---
title: 'Shockabsorber Example Chapter 8'
subtitle: 'Statistical Methods for Reliability Data'
output: 
  html_document:
    toc: yes
    toc_float: yes
    df_print: paged
---

This example walks through the analysis of the `shockabsorber` data set from the SMRD text, and shown in the table below.  

```{r, echo=2}
library(SMRD)
shockabsorber
```

The goal of this example is to outline the methods for constructing confidence intervals for the CDF $F(t|\mu,\sigma)$, the quantile function $F^{-1}(p|\mu,\sigma)$, and the hazard function $h(t|\mu,\sigma)$.  For simplicity, we will assume that the data can be aduquately modeled using a Weibulll distribution with pdf

$$
f(t|\mu,\sigma) = \Phi_{_{SEV}}\left(\frac{\log[t]-\mu}{\sigma}\right).
$$

Each of the functions for which we want to compute confidence intervals are themselves functions of the parameters $(\mu,\sigma)$.  Thus, we will be required to find the covariance matrix of the parameters. This can be easily done using the SMRD package by first creating a `life.data` object.  Note that we have ignored column 2 for this example as it is not important to model each failure mode separately.  

```{r}
shock.ld <- frame.to.ld(shockabsorber, 
                        response.column = 1, 
                        censor.column = 3)
```

Once the `life.data` object has been created, we need only invole the `mlest` function to create a list of maximum likelihood output.

```{r}
shock.ml <- print(mlest(shock.ld, 
                        distribution = 'weibull'))
shock.ml
```

Now we see that the maximum likelihood estimate $\widehat{\mu}_{_{MLE}}, \widehat{\sigma}_{_{MLE}}$ is captured as

```{r}
shock.ml$mle.table
```

And the covariance matrix is stored as

```{r}
shock.ml$vcv.matrix
```

## Computing Confidence Intervals for $F^{-1}(p|\mu,\sigma)$

The quantile function can be found by inverting the cdf.  For any log-location scale distribution the quantile function is expressed as 

$$
F^{-1}(p) = t_{p} = \exp\left[\Phi^{-1}(p)\sigma +\mu\right]
$$

In general the confidence intervals for $t_p$ are computed as

$$
\left[\underset{\sim}{t_p}, \overset{\sim}{t_p}\right]=\widehat{t_p}_{_{MLE}}\pm z_{_{(1-\alpha/2)}}se_{t_p}
$$

<small>
$$
\begin{aligned}
\widehat{se}_{\hat{g}_1}&=\sqrt{\widehat{Var}(\hat{g}_1)}\\
&=\left[\left(\frac{\partial g_1}{\partial\mu}\right)^2\widehat{Var}(\hat{\mu})+2\left(\frac{\partial g_1}{\partial\mu}\right)\left(\frac{\partial g_1}{\partial\sigma}\right)\widehat{Cov}(\hat{\mu},\hat{\sigma})+\left(\frac{\partial g_1}{\partial\sigma}\right)^2\widehat{Var}(\hat{\sigma})\right]^{1/2}
\end{aligned}
$$
</small>

```{r}
exp1 <- qsev(0.05)
exp2 <- shock.ml$mle[2,1]
exp3 <- shock.ml$mle[1,1]
exp.term <- (exp(exp1 * exp2 + exp3)) ^ 2

inner.term <- shock.ml$vcv[1,1] + 2 * qsev(0.05) * shock.ml$vcv[1,2] + qsev(0.05)^2 * shock.ml$vcv[2,2]

se.tp <- sqrt(inner.term * exp.term)

tp.mle <- exp(qsev(0.05) * shock.ml$mle[2,1] + shock.ml$mle[1,1])

tp.ci_low  <- tp.mle - qnorm(1-0.05/2) * se.tp
tp.ci_high <- tp.mle + qnorm(1-0.05/2) * se.tp

tp.ci <- c(tp.ci_low, tp.ci_high)

tp.ci
```

## Log transformed CI

```{r}
se.tp_log <- sqrt(inner.term * exp.term)/tp.mle

tp.mle_log <- log(tp.mle)

tp.ci_low_log  <- tp.mle_log - qnorm(1-0.05/2) * se.tp_log
tp.ci_high_log <- tp.mle_log + qnorm(1-0.05/2) * se.tp_log

tp.ci_log <- exp(c(tp.ci_low_log, tp.ci_high_log))

tp.ci_log
```

```{r}
exp(qnorm(1-0.05/2)*se.tp/tp.mle) -> w
log.ci <- c(tp.mle / w, tp.mle * w)

```
