---
title: 'Homework 8'
output:
  pdf_document: default
  html_document: default
date: "2023-05-29"
author: 'Brandon Hosley'
---
---
title: "Homework 8"
footer: 'HW 8'
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

```{r setup, include=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(xtable)
library(MASS)
library(readxl)
options(xtable.comment = FALSE, xtable.type="latex")
options(rgl.useNULL=TRUE)
#.rs.restartR()
library(qpcR)
library(kableExtra)
library(modelsummary)
library(car)
library(MuMIn)
library(ResourceSelection)
library(ggplot2)
library(latex2exp)
library(caret) 
library(tidyverse)
library(summarytools)
library(corrplot)
library(glue)
library(plyr)
library(performance)
library(glmnet)
library(BAS)
library(grt)
```

```{r, include=FALSE}
kable <- function(data, ...) {
  knitr::kable(data, ..., booktabs = TRUE, digits = 4, align = 'c',escape = FALSE) %>% 
    kable_styling(latex_options =c("hold_position"))
}

adjR2 <- function(model){
  summary(model)$adj.r.squared
} 

  # Execution Variables
ByPositions <- FALSE
```

# Outline of Empirical Modeling Project

## Introduction Section

The purpose of this report is to demonstrate proficiency in the course material by 
modeling NFL player performance to achieve utilizing the first pick in the most optimal way (probabilistic)

The league has ten fantasy teams, and I have the number one pick; and thus the 20 as well.
As such predicting top 20 players ensures that we can select at least two of those players.

Prioritizing consistency in performance. We will use average points per game as our metric.
Regress data from the 2020 and 2021 (can use 2019 as well), target is to predict 2022 performance.

```{r, include=FALSE}
df19 <- read_excel('./ProjectData.xlsx', sheet = '2019 Regular Season',
                   .name_repair = function(col){ gsub(" ", "_", col) })
df19 <- df19 %>% rename_at('PPG', ~'PPG.current')

df20 <- read_excel('./ProjectData.xlsx', sheet = '2020 Regular Season',
                   .name_repair = function(col){ gsub(" ", "_", col) })
df20 <- df20 %>% rename_at('PPG', ~'PPG.current')

df21 <- read_excel('./ProjectData.xlsx', sheet = '2021 Regular Season',
                   .name_repair = function(col){ gsub(" ", "_", col) })
df21 <- df21 %>% rename_at('PPG', ~'PPG.current')

df22 <- read_excel('./ProjectData.xlsx', sheet = '2022 Regular Season',
                   .name_repair = function(col){ gsub(" ", "_", col) })
df22 <- df22 %>% rename_at('PPG', ~'PPG.current')

All.features <- c(colnames(df21))
```

# Data Exploration

## Data Quality

```{r}
paste('Stats for season 2019 :', sum(is.na(df19)))
summary(df19)
paste('Stats for season 2020:', sum(is.na(df20)))
summary(df20)
paste('Stats for season 2021:', sum(is.na(df21)))
summary(df21)
```


## Exploration of Team Performance

### Average PPG in teams

```{r}
teams.average.PPG.all <- Reduce(
  function(x, y, ...) merge(x, y, by = 'Team', all = TRUE, ...), list(
    aggregate(PPG.current ~ Team, df19, mean),
    aggregate(PPG.current ~ Team, df20, mean), 
    aggregate(PPG.current ~ Team, df21, mean)) ) %>% 
  set_names(., c('Team','2019','2020','2021'))  %>% 
  #arrange(mean('2019','2020','2021')) %>%
  gather(key = "Year", value = "Average.PPG", -Team)

team.levels <- aggregate(Average.PPG ~ Team, teams.average.PPG.all, mean)
team.levels <- t(team.levels[order(team.levels$Average.PPG),])
```

### All PPG

```{r}
teams.average.PPG.all$Team <- factor(teams.average.PPG.all$Team, levels = team.levels, ordered=TRUE)
df19$Team <- factor(df19$Team, levels =team.levels, ordered=TRUE)
df20$Team <- factor(df20$Team, levels =team.levels, ordered=TRUE)
df21$Team <- factor(df21$Team, levels =team.levels, ordered=TRUE)

violin_a = 0.3
teamViolinPlot <- ggplot(df19, aes(Team, PPG.current)) + geom_violin(aes(colour = "2019"), alpha = violin_a) + 
  geom_violin(df20, mapping = aes(Team, PPG.current, colour = "2020"), position = position_nudge(x = 0), alpha = violin_a) +
  geom_violin(df21, mapping = aes(Team, PPG.current, colour = "2021"), position = position_nudge(x = 0), alpha = violin_a) +
  geom_point(teams.average.PPG.all, mapping = aes(Team, Average.PPG, color = Year), alpha = violin_a+0.2)

ggsave(teamViolinPlot, filename="Figures/Team_PPGs_YearOn.png", dpi=300, width = 12, height = 6)
```

It does not appear that there are any significant underlying relations with teams.

## Exploration of Player Performance

One of the major difficulties will be making legitimate comparisons given the different positions that play are likely to earn points via different features.

### Within Single Year

```{r}
df2019.gathered <- df19 %>% 
  select(c(-Name,-Team)) %>%
  mutate(PPG.2019 = PPG.current) %>%
  as_data_frame() %>%
  gather(key = "variable", value = "value", -PPG.current, -Position )

featurePlot2019 <- ggplot(df2019.gathered, aes(x = value, y = PPG.current) ) +
  geom_point(aes(color = Position)) +
  facet_wrap(~variable, ncol = 3, scales = 'free_x') + 
  theme(aspect.ratio = 1, axis.ticks.x=element_blank() ) 

ggsave(featurePlot2019, filename="Figures/feature_comparison_2019.png", dpi=300, width = 8, height = 11)
```

### Players Across Seasons

```{r}
df19_pred20 <- inner_join(df19, df20[c('Name','PPG.current')], by='Name', suffix = c('.2019', '.2020') ) %>%
  rename_at('PPG.current.2019', ~'PPG.current') %>%
  rename_at('PPG.current.2020', ~'PPG.next') %>%
  select(c(-Name,-Team)) %>%
  as_data_frame() %>%
  gather(key = "variable", value = "value", -PPG.next, -Position )

data2019pred2020 <- ggplot(df19_pred20, aes(x = value, y = PPG.next)) +
  geom_point(aes(color = Position)) +
  facet_wrap(~variable, ncol = 3, scales = 'free_x') + 
  theme(aspect.ratio = 1, axis.ticks.x=element_blank() ) 

ggsave(data2019pred2020, filename="Figures/2019_predicting_2020.png", dpi=300, width = 8, height = 11)
```

```{r}
df20_pred21 <- inner_join(df20, df21[c('Name','PPG.current')], by='Name', suffix = c('.2020', '.2021') ) %>%
  rename_at('PPG.current.2020', ~'PPG.current') %>%
  rename_at('PPG.current.2021', ~'PPG.next') %>%
  select(c(-Name,-Team,-Total)) %>%
  as_data_frame() %>%
  gather(key = "variable", value = "value", -PPG.next, -Position )

data2020pred2021 <- ggplot(df20_pred21, aes(x = value, y = PPG.next)) +
  geom_point(aes(color = Position)) +
  facet_wrap(~variable, ncol = 3, scales = 'free_x') + 
  theme(aspect.ratio = 1, axis.ticks.x=element_blank() ) 

ggsave(data2020pred2021, filename="Figures/2020_predicting_2021.png", dpi=300, width = 8, height = 11)
```

The colors used are:
```{r}
FB.color <- "#F8766D" 
QB.color <- "#A3A500" 
RB.color <- "#00BF7D" 
TE.color <- "#00B0F6" 
WR.color <- "#E76BF3"
```


## Position Based Modeling

Combine the seasons.

```{r}
names(df19_pred20) <- c('Position','PPG.next','variable','value')
names(df20_pred21) <- c('Position','PPG.next','variable','value')
combined.pseudopreds <- rbind(df19_pred20, df20_pred21) %>% 
  mutate(variable = recode(variable, PPG.2019 = 'PPG.current', PPG.2020 = 'PPG.current' ))
```

### Quarterback

#### Individual Features

```{r, eval = ByPositions}
QB.featureSet <- All.features[!All.features %in% c('Receiving_TD','Receiving_Yards','Receptions')]
QB.plot <- ggplot(subset(combined.pseudopreds, (Position == 'QB') & (variable %in% QB.featureSet) ),
                  aes(x = value, y = PPG.next)) +
  geom_point(color=QB.color) +
  facet_wrap(~variable, ncol = 3, scales = 'free_x') + 
  theme(aspect.ratio = 1, axis.ticks.x=element_blank() ) 

ggsave(QB.plot, filename="Figures/QB_plot.png", dpi=300, width = 8, height = 11)
```

#### Correlation

```{r, eval = ByPositions}
png(filename = "Figures/QB_plot_corr.png", width = 1200, height = 800)
inner_join(df20[QB.featureSet], df21[c('Name','PPG.current')], by='Name', suffix = c('.2020', '.2021')) %>%
  rename_at('PPG.current.2020', ~'PPG.current') %>%
  rename_at('PPG.current.2021', ~'PPG.next') %>%
  filter(Position == 'QB') %>%
  select(c(-Name,-Team,-Position)) %>%
  as_data_frame() %>%
  cor() %>% 
  corrplot();

dev.off()
```


### Running Back

#### Individual Features

```{r, eval = ByPositions}
RB.featureSet <- All.features[!All.features %in% c('Passing_INT','Passing_TD','Passing_Yards')]
RB.plot <- ggplot(subset(combined.pseudopreds, (Position == 'RB') & (variable %in% RB.featureSet) ),
                  aes(x = value, y = PPG.next)) +
  geom_point(color=RB.color) +
  facet_wrap(~variable, ncol = 3, scales = 'free_x') + 
  theme(aspect.ratio = 1, axis.ticks.x=element_blank() ) 

ggsave(RB.plot, filename="Figures/RB_plot.png", dpi=300, width = 8, height = 11)
```

#### Correlation

```{r, eval = ByPositions}
png(filename = "Figures/RB_plot_corr.png", width = 1200, height = 800)
inner_join(df20[RB.featureSet], df21[c('Name','PPG.current')], by='Name', suffix = c('.2020', '.2021')) %>%
  rename_at('PPG.current.2020', ~'PPG.current') %>%
  rename_at('PPG.current.2021', ~'PPG.next') %>%
  filter(Position == 'RB') %>%
  select(c(-Name,-Team,-Position)) %>%
  as_data_frame() %>%
  cor() %>% 
  corrplot();

dev.off()
```


### Tight End

#### Individual Features

```{r, eval = ByPositions}
TE.featureSet <- All.features[!All.features %in% c('Passing_INT','Passing_TD','Passing_Yards')]
TE.plot <- ggplot(subset(combined.pseudopreds, (Position == 'TE') & (variable %in% TE.featureSet) ),
                  aes(x = value, y = PPG.next)) +
  geom_point(color=TE.color) +
  facet_wrap(~variable, ncol = 3, scales = 'free_x') + 
  theme(aspect.ratio = 1, axis.ticks.x=element_blank() ) 

ggsave(TE.plot, filename="Figures/TE_plot.png", dpi=300, width = 8, height = 11)
```

#### Correlation

```{r, eval = ByPositions}
png(filename = "Figures/TE_plot_corr.png", width = 1200, height = 800)
inner_join(df20[TE.featureSet], df21[c('Name','PPG.current')], by='Name', suffix = c('.2020', '.2021')) %>%
  rename_at('PPG.current.2020', ~'PPG.current') %>%
  rename_at('PPG.current.2021', ~'PPG.next') %>%
  filter(Position == 'TE') %>%
  select(c(-Name,-Team,-Position)) %>%
  as_data_frame() %>%
  cor() %>% 
  corrplot();

dev.off()
```


### Wide Receiver

#### Individual Features

```{r, eval = ByPositions}
WR.featureSet <- All.features[!All.features %in% c('Passing_INT','Passing_TD','Passing_Yards','Rushing_TD')]
WR.plot <- ggplot(subset(combined.pseudopreds, (Position == 'WR') & (variable %in% WR.featureSet) ),
                  aes(x = value, y = PPG.next)) +
  geom_point(color=WR.color) +
  facet_wrap(~variable, ncol = 3, scales = 'free_x') + 
  theme(aspect.ratio = 1, axis.ticks.x=element_blank() ) 

ggsave(WR.plot, filename="Figures/WR_plot.png", dpi=300, width = 8, height = 11)
```

#### Correlation

```{r, eval = ByPositions}
png(filename = "Figures/WR_plot_corr.png", width = 1200, height = 800)
inner_join(df20[WR.featureSet], df21[c('Name','PPG.current')], by='Name', suffix = c('.2020', '.2021')) %>%
  rename_at('PPG.current.2020', ~'PPG.current') %>%
  rename_at('PPG.current.2021', ~'PPG.next') %>%
  filter(Position == 'WR') %>%
  select(c(-Name,-Team,-Position)) %>%
  as_data_frame() %>%
  cor() %>% 
  corrplot();

dev.off()
```


# Variable Selection

```{r}
All.19to20 <- inner_join(df19, df20[c('Name','PPG.current')], by='Name', suffix = c('.2019', '.2020')) %>%
  rename_at('PPG.current.2019', ~'PPG.current') %>%
  rename_at('PPG.current.2020', ~'PPG.next')

All.20to21 <- inner_join(df20, df21[c('Name','PPG.current')], by='Name', suffix = c('.2020', '.2021')) %>%
  rename_at('PPG.current.2020', ~'PPG.current') %>%
  rename_at('PPG.current.2021', ~'PPG.next')
  
All.19to21 <- rbind.fill(All.19to20,All.20to21) %>% replace(is.na(.), 0) %>% as_data_frame()
```

## Techniques Tried But Ultimately Unused

1. Dredge took a really long time and did not provide any better of results.

```{}
library(leaps)
# Set seed for reproducibility
set.seed(123)
# Set up repeated k-fold cross-validation
train.control <- trainControl(method = "cv", number = 10)
# Train the model
step.model <- train(PPG.next ~., data = QB.train,
                    method = "leapSeq", 
                    tuneGrid = data.frame(nvmax = 1:length(QB.featureSet)),
                    trControl = train.control
                    )
step.model$results
summary(step.model$finalModel)
```

2. The leaps library for subsetting returned less effective models.

3. GLM provided a reasonable LASSO Regression, so it was implemented below.

## Create Functions

These functions were originally built with the QB segment of the data, but generalized for broad implementation.

```{r}
  # Generate a position-specific dataset.
training.set <- function(position){
  All.19to21 %>%
  filter(Position == position) %>%
  select(c(-Name,-Team,-Position)) %>%
  as_data_frame()
} 
  # Save and export the model parameters
save.summary <- function(mod){
  filename <- glue('Tables/{deparse(substitute(mod))}.tex')
  xtable(summary(mod)) %>%
  knitr::kable(., format = 'latex') %>%
  writeLines(., filename)
}
  # Technically actually, elasticnet
lasso <- function(dataset, a = 1){
  cv.model <- cv.glmnet(x = as.matrix(subset(dataset, select = -c(PPG.next))), 
                        y = dataset$PPG.next, alpha = a)
  best.lambda <- cv.model$lambda.min
  best.model <- glmnet(x = as.matrix(subset(dataset, select = -c(PPG.next))), 
                       y = dataset$PPG.next, alpha = a, lambda = best.lambda)
  out <- list(cv=cv.model, mod=best.model)
  return(out)
}
  # Feature selection in both directions from a full model
stepwise <- function(full_model){
  stepAIC(full_model, direction = "both", trace = FALSE)
}
  # Bayes linear model
bayesglm <- function(dataset){
  bas.lm(PPG.next ~ ., data = dataset, prior = "BIC", 
                 modelprior = Bernoulli(1), 
                 include.always = ~ ., n.models = 1)
}

```

## Quarterbacks

```{r, eval = ByPositions}
  # QB dataset
QB.train <- training.set('QB')

  # Check for Outliers
check_outliers(QB.train)

  # Train a full QB model
QB.mod.full <- lm(PPG.next ~. , data = QB.train, na.action=na.pass)
print('Full')
summary(QB.mod.full)

  # Train a Regularized Regression
QB.lasso <- lasso(QB.train)
plot(QB.lasso$cv)
print('Regular')
coef(QB.lasso$mod)
print(QB.lasso$mod$dev.ratio)

  # Train by Step
QB.mod.step <- stepwise(QB.mod.full)
print('Step')
summary(QB.mod.step)

  # Train a Bayesian Linear Model
QB.mod.bayes <- bayesglm(QB.train)
print('Bayes')
summary(QB.mod.bayes)
```

The outliers found here are (both 2020 season)
Taysom Hill O ~ 9.8 PPG.next
Dak Prescot ~ 5 Games, 20.0 PPG.next


## Running Backs

```{r, eval = ByPositions}
  # RB dataset
RB.train <- training.set('RB')

  # Check for Outliers
try(check_outliers(RB.train))

  # Train a full RB model
RB.mod.full <- lm(PPG.next ~. , data = RB.train, na.action=na.pass)
print('Full')
summary(RB.mod.full)

  # Train a Regularized Regression
RB.lasso <- lasso(RB.train)
plot(RB.lasso$cv)
print('Regular')
coef(RB.lasso$mod)
print(RB.lasso$mod$dev.ratio)

  # Train by Step
RB.mod.step <- stepwise(RB.mod.full)
print('Step')
summary(RB.mod.step)

  # Train a Bayesian Linear Model
RB.mod.bayes <- bayesglm(RB.train)
print('Bayes')
summary(RB.mod.bayes)
```


## Tight End

```{r, eval = ByPositions}
  # TE dataset
TE.train <- training.set('TE')

  # Check for Outliers
try(check_outliers(TE.train))

  # Train a full TE model
TE.mod.full <- lm(PPG.next ~. , data = TE.train, na.action=na.pass)
print('Full')
summary(TE.mod.full)

  # Train a Regularized Regression
TE.lasso <- lasso(TE.train)
plot(TE.lasso$cv)
print('Regular')
coef(TE.lasso$mod)
print(TE.lasso$mod$dev.ratio)

  # Train by Step
TE.mod.step <- stepwise(TE.mod.full)
print('Step')
summary(TE.mod.step)

  # Train a Bayesian Linear Model
TE.mod.bayes <- bayesglm(TE.train)
print('Bayes')
summary(TE.mod.bayes)
```

## Wide Receiver

```{r, eval = ByPositions}
  # WR dataset
WR.train <- training.set('WR')

  # Check for Outliers
try(check_outliers(WR.train))

  # Train a full WR model
WR.mod.full <- lm(PPG.next ~. , data = WR.train, na.action=na.pass)
print('Full')
summary(WR.mod.full)

  # Train a Regularized Regression
WR.lasso <- lasso(WR.train)
plot(WR.lasso$cv)
print('Regular')
coef(WR.lasso$mod)
print(WR.lasso$mod$dev.ratio)

  # Train by Step
WR.mod.step <- stepwise(WR.mod.full)
print('Step')
summary(WR.mod.step)

  # Train a Bayesian Linear Model
WR.mod.bayes <- bayesglm(WR.train)
print('Bayes')
summary(WR.mod.bayes)
```



# Consolidating the Model Pieces


```{r}
Scaled.train.x <- scale(select(All.19to21,-c(Name,Position,Team,PPG.next)))
Scaled.train.y <- scale(select(All.19to21, PPG.next))
```


```{r}
All.train <- merge(All.19to21$Position, cbind(Scaled.train.x,Scaled.train.y), by = "row.names", all = TRUE) %>%
  as_data_frame() %>% rename_at('x', ~'Position') %>% select(-Row.names)


All.mod.full <- lm(PPG.next ~(.)*Position , data = All.train, na.action=na.pass)
summary(All.mod.full)
```

```{r}
All.bayes <- bayesglm(All.train)
summary(All.bayes)
```

## Checking for Outliers
(analysis of influential observations)

```{r}
check_outliers(All.train)
check_outliers(All.mod.full)
```

```{r}
data_outliers <- c(1, 57, 112, 118, 119, 121, 122, 123, 125, 126, 
                   127, 128, 129, 136, 142, 149, 157, 182, 235, 254, 
                   297, 335, 353, 354, 370, 379, 396) 
model_outliers <- c(229, 379)

print('With Data Outliers Removed')
All.mod.out <- lm(PPG.next ~(.)*Position , data = All.train[-data_outliers,], na.action=na.pass)
summary(All.mod.out)
check_outliers(All.mod.out)

print('With Model Outliers Removed')
All.mod.out <- lm(PPG.next ~(.)*Position , data = All.train[-model_outliers,]%>%select(-c(Receiving_Yards,Games,Passing_INT,Fumbles_Lost)), na.action='na.omit')
summary(All.mod.out)
check_outliers(All.mod.out)
```



```{r}
vif(All.mod.out, type='predictor')
#alias(All.mod.out)

```


```{r}
library(gt)  
library(gtsummary)
All.mod.out %>%
  gtsummary::tbl_regression() %>%
  gtsummary::modify_caption('Summary of Multi-regression Model')%>%
  knitr::kable(., format = 'latex') %>%
  writeLines(., 'Tables/Multiple-Regression_coeffs.tex')

```


```{r} 
All.train.adj <- All.train[-model_outliers,]

All.19to21[model_outliers,] %>%
  knitr::kable(., format = 'latex') %>%
  writeLines(., 'Tables/Outliers.tex')
```


## Model Adequacy

```{r}
qqPlot(residuals(All.mod.out), main = 'QQ-plot of Multi-regression Model', ylab = 'Residuals', xlab = 'Normal Quantiles')

#ggsave(plot, filename="Figures/results_plot.png", dpi=300, width = 9, height = 8)
```


```{r}
gathered.residuals <- cbind(All.train.adj, Residuals = residuals(All.mod.out))  %>%
  as_data_frame() %>%
  gather(key = "variable", value = "value", -Position, -Residuals )

all.residual.plot <- ggplot(gathered.residuals, aes(x = value, y = Residuals)) +
  geom_point(aes(color = Position)) +
  facet_wrap(~variable, ncol = 3, scales = 'free_x') + 
  theme(aspect.ratio = 1, axis.ticks.x=element_blank() ) 

all.residual.plot
ggsave(all.residual.plot, filename="Figures/residual_plot.png", dpi=300, width = 8, height = 11)
```






```{r}
df22.test <- cbind.data.frame(select(df21, c(Name,Team,Position)), scale(select(df21, colnames(Scaled.train.x)), 
                     center = attr(Scaled.train.x, 'scaled:center'), 
                     scale = attr(Scaled.train.x, 'scaled:scale') )  ) %>%
  inner_join(., df22[c('Name','PPG.current')], by='Name', suffix = c('.2021', '.2022') ) %>%
  rename_at('PPG.current.2021', ~'PPG.current') %>%
  rename_at('PPG.current.2022', ~'PPG.actual') %>%
  as_data_frame()

df22.scaled.preds <- predict(All.mod.out, select(df22.test, -c(Name,Team,PPG.actual)))
df22.test$PPG.preds <- df22.scaled.preds * attr(Scaled.train.y, 'scaled:scale') + attr(Scaled.train.y, 'scaled:center')

results.plot <- ggplot(df22.test, aes(x=PPG.preds, y=PPG.actual)) + 
  geom_point(aes(color=Position)) +
  geom_abline(aes(slope = 1, intercept = 0), linetype = 2) + ggtitle('Model Predictions vs. Ground Truth') +
  xlab('Predicted PPG') + ylab("Actual PPG")


results.plot
ggsave(results.plot, filename="Figures/results_plot.png", dpi=300, width = 9, height = 8)


data <- data.frame(pred = df22.test$PPG.preds, actual = df22.test$PPG.actual)
mean((data$actual - data$pred)^2)
```

```{r}
select(df22.test[order(df22.test$PPG.actual, decreasing = TRUE),][1:21,], c(Name,Team,Position,PPG.actual,PPG.preds))
select(df22.test[order(df22.test$PPG.preds, decreasing = TRUE),][1:21,], c(Name,Team,Position,PPG.actual,PPG.preds))
```




```{r}
df22.trunc <- rbind.data.frame(
  df22.test[order(df22.test$PPG.actual, decreasing = TRUE),][1:21,], 
  df22.test[order(df22.test$PPG.preds, decreasing = TRUE),][1:21,]) %>%
  unique

results.trunc.plot <- ggplot(df22.trunc, aes(x=PPG.preds, y=PPG.actual)) + 
  geom_point(aes(color=Position)) +
  geom_abline(aes(slope = 1, intercept = 0), linetype = 2) + ggtitle('Model Predictions vs. Ground Truth (Top 21 as inclusive or)') +
  xlab('Predicted PPG') + ylab("Actual PPG")

results.trunc.plot
ggsave(results.trunc.plot, filename="Figures/results_trunc_plot.png", dpi=300, width = 9, height = 8)
```


```{r}
plotRanks <- function(a, b, labels.offset=0.1, arrow.len=0.2)
  {
  xadj.1 = 0.3
  xadj.2 = xadj.1 + 0.3
  
  len.1 <- length(a)
  len.2 <- length(b)
  a.to.b <- match(a, b)
  # Set up the eenvironment
  p <- ggplot() + theme_void() + 
    theme(plot.title = element_text(hjust = 0.5)  ) + 
    xlim(0, xadj.2+0.3) + ylim(0, max(len.1, len.2)) +
    # Labels
    labs(title = 'Top PPG Rankings for 2023 NFL Season (by PPG)') +
    annotate("text", x = 0.08, y = 12, label = 'Predicted', angle = 90, cex=5) +
    annotate("text", x = 0.83, y = 12, label = 'Actual', angle = -90, cex=5) +
    # Add the points
    geom_point(aes(rep(xadj.1 , len.1),1:len.1)) +
    geom_point(aes(rep(xadj.2 , len.2), 1:len.2)) + 
    # Add the names of the players
    geom_text(aes(rep(xadj.1 -labels.offset, len.1), 1:len.1, label=a), nudge_x = 0.1) +
    geom_text(aes(rep(xadj.2 +labels.offset, len.2), 1:len.2, label=b), nudge_x = -0.1) +
    # Draw arrows between the same players
    geom_segment(aes(rep(xadj.1+0.02, len.1), 1:len.1, xend= rep(xadj.2-0.02, len.2), yend= a.to.b,),
                 arrow = arrow(length=unit(arrow.len,'cm'), angle=20) )
  return(p) 
}

ranks <- plotRanks(  rev(select(df22.test[order(df22.test$PPG.preds, decreasing = TRUE),],Name)$Name[1:21]) ,
                     rev(select(df22.test[order(df22.test$PPG.actual, decreasing = TRUE),],Name)$Name[1:21]) , labels.offset = 0.2 )
ranks
ggsave(ranks, filename="Figures/ranks_plot.png", dpi=300, width = 9, height = 8)
```







