---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 3 Practical Exercise"
footer: `r paste('Lesson 3 Practical Exercise')`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(xtable)
options(xtable.comment = FALSE, xtable.type="latex")
```

## a) Read data from data-ex-2-1.xlsx using the read.xlsx() command.

```{r, echo=T}
df <- read.xlsx('../Practical 1/data-ex-2-1.xlsx', sheetIndex = 1)
```

## b) Give names to columns using names() command and attach to the dataframe using attach(). Output data to make sure it reads properly using print(xtable(\textit{dataname}))
```{r, echo=T}
names(df) <- c("Observation", "ShearStrength","Age")
attach(df)
```

## c) Output data structure and dimensions using the str() and dim() commands.
```{r, echo=T}
sprintf('The data structure is a %s', typeof(df) )
sprintf('The dimensions are %i by %i', dim(df)[1], dim(df)[2])
```

## d) Create any baseline model(s) necessary to complete Examples 2.5, 2.6, and 2.7
```{r, echo=T}
mod <- lm(ShearStrength ~ Age)
summary(mod)
print(anova(mod))
```

# 2. Example 2.5 (p. 30)
## a) Construct a 95% confidence interval for the slope parameter (by hand)
```{r, echo=T}
H <- sqrt(997.94/(4.060311**2))
CI_lower <- 65.097647 - H
CI_upper <- 65.097647 + H

sprintf('Upper: %f   Lower: %f', CI_upper, CI_lower)
```

## b) Check using Confint command
```{r, echo=T}
confint(mod)
```

# 3. Example 2.6 (p.31-32)
## a) Construct 95% C.I. for the point $x_0$ = 13.3625.
```{r, echo=T}
x_0_upper = 73.62804500+ 13.3625*-0.02030779
x_0_lower = 56.56724954- 13.3625*-0.02823887

sprintf('Upper: %f   Lower: %f', x_0_upper, x_0_lower)
```

# 4. Example 2.7 (p.34-35)
## a) Construct a 95% prediction interval for $x_0$ = 10 weeks.
```{r, echo=T}
x_0_upper = 73.62804500+ 10*-0.02030779
x_0_lower = 56.56724954- 10*-0.02823887

sprintf('Upper: %f   Lower: %f', x_0_upper, x_0_lower)
```

## b) Reproduce Figure 2.5. First, create the scatterplot using plot(). Then add a line for the predicted values using lines(). Finally, add prediction interval lines and confidence interval lines using lines() and predict().
```{r, echo=T}
x <- df[,3]
y <- df[,2]


plot(x[order(x)],y[order(x)])

predict.fit <- predict(mod, interval="prediction", level=0.95)
confidence.fit  <- predict(mod, interval="confidence", level=0.95)

lines(x[order(x)], predict.fit[,1][order(x)])


lines(x[order(x)],predict.fit[,2][order(x)])
lines(x[order(x)],predict.fit[,3][order(x)])

lines(x[order(x)],confidence.fit[,2][order(x)])
lines(x[order(x)],confidence.fit[,3][order(x)])
```

