\documentclass[answers]{exam}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath,amssymb,amsthm}

\title{STAT 587 - Introduction to Probability and Statistics%
	\\ Homework 4}
\author{Brandon Hosley}
\date{\today}

\begin{document}
\maketitle
\begin{questions}

%%%%%%%%%%%%%%
%	\begin{ Question 1}	  %
%%%%%%%%%%%%%%
\question 
Let \(X_1,X_2,X_3\) and \(X_4\) be independent random variables, each having the same distribution with mean 5 and standard deviation 3, and let \(Y = X_1+2X_2+X_3-X_4\). Find \(\operatorname{Var}[Y]\).
\begin{solution}
	S
\end{solution}
%\end{ Question 1}

%%%%%%%%%%%%%%
%	\begin{ Question 2}	  %
%%%%%%%%%%%%%%
\question 
Suppose the joint pdf of lifetimes of a certain part and a spare is given by \(f(x,y) =e^{-(x+y)}\)
for \(0 < x\) and \(0 < y\) and zero otherwise. Find \(P(X<Y)\).
\begin{solution}
	S
\end{solution}
%\end{ Question 2}

%%%%%%%%%%%%%%
%	\begin{ Question 3}	  %
%%%%%%%%%%%%%%
\question 
Suppose $X$ and $Y$ are continuous random variables with joint pdf \(f(x,y) = 60x^2y\)
for \(0<x,0<y\) and \(x+y<1\) and zero otherwise. Find \(P(Y > 0.1 | X = 0.5)\).
\begin{solution}
	S
\end{solution}
%\end{ Question 3}

%%%%%%%%%%%%%%
%	\begin{ Question 4}	  %
%%%%%%%%%%%%%%
\question 
Suppose $X$ and $Y$ are continuous random variables with joint pdf \(f(x,y) = 24xy\)
if \(0<x,0<y\) and \(x+y<1\) and zero otherwise. Find \(\operatorname{Cov}[3X,5Y]\).
\begin{solution}
	S
\end{solution}
%\end{ Question 4}

%%%%%%%%%%%%%%
%	\begin{ Question 5}	  %
%%%%%%%%%%%%%%
\question 
Suppose that the conditional distribution of $Y$ given $X=x$ is Poisson with mean 
\(E[Y|x] = x , Y|x\sim\operatorname{POI}(x)\) and that \(X\sim\operatorname{EXP}(1)\). Find \(\operatorname{Var}[Y]\).
\begin{solution}
	S
\end{solution}
%\end{ Question 5}

%%%%%%%%%%%%%%
%	\begin{ Question 6}	  %
%%%%%%%%%%%%%%
\question 
Let \(f(x,y) = 6x\) for \(0<x<y<1\) and zero otherwise. Find \(f_1(x)\).
\begin{solution}
	S
\end{solution}
%\end{ Question 6}

%%%%%%%%%%%%%%
%	\begin{ Question 7}	  %
%%%%%%%%%%%%%%
\question 
Let $X$ be the number of customers arriving in a given minute at the drive-up window of a local bank, and let $Y$ be the number who make withdrawals. Assume that $X$ is Poisson distributed with expected value \(E[X]=3\), and that the conditional expectation and variance of $Y$ given \(X=x\) are \(E[Y|x] = x/2\) and \(\operatorname{Var}[Y|x]=(x+1)/3\). Find \(E[XY]\).
\begin{solution}
	S
\end{solution}
%\end{ Question 7}

%%%%%%%%%%%%%%
%	\begin{ Question 8}	  %
%%%%%%%%%%%%%%
\question 
If $X$ and $Y$ are discrete random variables with joint pdf \(f(x,y) = c\frac{2^{x+y}}{x!y!}\) 
for \(x=0,1,2,\ldots\) and \(y=0,1,2,\ldots\) and zero otherwise. Find $c$.
\begin{solution}
	S
\end{solution}
%\end{ Question 8}

%%%%%%%%%%%%%%
%	\begin{ Question 9}	  %
%%%%%%%%%%%%%%
\question 
Suppose $X$ and $Y$ are continuous random variables with joint pdf
\(f(x,y)= 24xy\) if \(0<x,0<y,\) and \(x+y<1\) and zero otherwise. Find\(E[XY]\).
\begin{solution}
	S
\end{solution}
%\end{ Question 9}

%%%%%%%%%%%%%%
%	\begin{ Question 10}	  %
%%%%%%%%%%%%%%
\question 
Suppose $X$ and $Y$ are continuous random variables with joint pdf
\(f(x,y) = 60x^2y\) for \(0<x,0<y\), and \(x+y<1\) and zero otherwise. Find the
conditional pdf of $Y$ given \(X=x\).
\begin{solution}
	S
\end{solution}
%\end{ Question 10}

\end{questions}
\end{document}