---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 6 Practical Exercise"
footer: `r paste('Lesson 6 Practical Exercise')`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(xtable)
options(xtable.comment = FALSE, xtable.type="latex")
```

# Perform data housekeeping - upload (same data as Example 3.1), name columns, display to make sure it reads properly, etc. 

```{r, echo=T}
df <- read.xlsx('../Practical 4/data-ex-3-1.xlsx', sheetIndex = 1)
```

```{r, echo=TRUE}
names(df) <- c("Observation", "Time","Cases", "Distance")
```

# 2. Example 4.1 (p.135-136)
## a) Calculate residuals and compare to Column (1) in Table 4.1, p. 137. 

```{r, echo=T}
mod <- lm(Time~Cases+Distance, data=df)
res <- data.frame(residuals(mod))
names(res) <- c('residuals')
```

##  b)Calculate standardized residuals using Equation 4.2;compare to Column (2) in Table 4.1, p. 137. 

```{r, echo=T}
MSE <- sum(res$residuals**2)/(nrow(res)-1-2)
res['Standardized'] <- res$residuals/sqrt(MSE) # One for the header, two for the parameters
res['Standardized']
```

##  c)Calculate studentized residuals using Equation 4.8; compare to Column (3) in Table 4.1, p. 137. 

```{r, echo=T}
library(MASS)
matx <- as.matrix(df[3:4])
X <- cbind(matx, c(rep(1,nrow(df))))

h_func <- function(row) t(row) %*% ginv(t(X) %*% X) %*% row
h_vec <- vector()
for (row in 1:nrow(X)) {
  h_vec[row] <- h_func(X[row,])
}

res['h_ii'] <- h_vec
res['Studentized'] <- res$residuals/sqrt(MSE*(1-res$h_ii))
res['Studentized']
```

## d) Calculate PRESS residuals using Equation 4.11; compare to Column (5) in Table 4.1, p. 137. 

```{r, echo=T}
res['PRESS'] <- res$residuals/(1-res$h_ii)
res['PRESS']
```

## e)Calculate R-Student residuals using Equations 4.12 and 4.13; compare to Column (6) in Table 4.1, p. 137. Looks good.

```{r, echo=T}
s2i <- ((nrow(res)-ncol(X)-1)*MSE - (res$residuals**2/(1-res$h_ii)) )/(nrow(res)-ncol(X)-2) # Subtract one more due to intercepts in X
res['R-Student'] <- res$residuals/sqrt(s2i*(1-res$h_ii))
res['R-Student']
```

## f) Reproduce Table 4.1 on p. 137 - Consolidate above vectors into a dataframe using data.frame(). Give column names using colnames() and c().

```{r, echo=T}
show(res)
```



Note: R has functions called rstandard() and rstudent(). Note that rstandard() outputs what the textbook calls Studentized Residuals
and rstudent() outputs what the textbook calls R-Student residuals or 'externally studentized' residuals. Don't get confused. 
Compare your manually-computer vectors above with the rstandard() and rstudent() functions. The rounded difference should be a vector of zeros. 



# 3. Example 4.2 (p. 139-140)
## a)Create plot of residuals against fitted y_hat values for each type of residual calculated in Example 4.1 using plot()

```{r, echo=T}
plot(x=predict(mod), y=res$residuals)
```

## b) Create normal probability plot of residuals using qqnorm()

```{r, echo=T}
qqnorm(x=predict(mod), y=res$residuals)
```

# 4. Example 4.3 (p. 141)
## a) Create a plot of residuals against the each of the regressors (Use R-Student residuals)

```{r, echo=T}
plot(x=predict(mod), y=res$Studentized)
```

# 5. Example 4.5 (p. 144) ###
## a) Create partial regression plots for each of the two regressors. Use rstudent() to calculate residuals.

```{r, echo=T}

```

# 6. Example 4.6 (p.151-152) ###
## a) Calculate PRESS Statistic and R-Squared_PRESS (by hand)

```{r, echo=T}

```
