---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 18 Practical Exercise"
footer: `r paste('Lesson 18 Practical Exercise')`
date: "`r format(as.Date(c('2021/05/26')), '%d %B %Y')`"
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
library(kableExtra)
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(readxl)
library(printr)
library(xtable)
library(formatR)
library(lmtest)
library(orcutt)
options(xtable.comment = FALSE, xtable.type="latex")
```

```{r, include=FALSE}
kable <- function(data, ...) {
  knitr::kable(data, ..., format = 'latex', booktabs = TRUE, digits = 5, align = 'c') %>% 
    kable_styling( latex_options =c("hold_position") )
}
```

# Perform data housekeeping - upload data for Examples 14.1 and 14.3; name columns, display to make sure it reads properly, etc. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df1 <- read_excel('./data-ex-14-1.xlsx')
names(df1) <- c("Year", "T", "Sales", "Expenditures")

df3 <- read_excel('./data-ex-14-3.xlsx')
names(df3) <- c("Time", "MarketShare", "Price")
```

# 2. Example 14.1 
## a) Initially assume straight-line relationship; create scatterplot and linear model; compare results to Figure 14.1 and Table 14.2 on p. 479.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(df1$Expenditures, df1$Sales, xlab = "Expenses",
  ylab = "Sales", main = "Example 14.1 Scatterplot")
mod <- lm(Sales ~ Expenditures, data = df1)
kable(xtable(summary(mod)))
kable(anova(mod))
```

## b) Plot R-Student residuals versus order of observations; compare to Figure 14.1 on p. 479.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
R_Student <- rstudent(mod)
plot(df1$T, R_Student, xlab = "Time (Years)", ylab = "Residuals",
     main = "Time Series Plot of Residuals")
lines(df1$T, R_Student)
```

## c) Perform Durbin-Watson test automatically using dwtest().

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df1_dw <- dwtest(df1$Sales ~ df1$Expenditures, order.by = df1$Year)
kable(xtable(summary(df1_dw)))
df1_dw
```

## d) Calculate Durbin-Watson test statistic using Equation 14.5.The sum() and sapply() functions may be helpful. Compare to p. 480.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
dw_num <- sum(sapply(2:(length(df1$Year)), function(x) {
  sum(mod$residuals[x] - mod$residuals[x - 1])^2 }))

dw_den <- sum(mod$residuals^2)
dw_statistic <- dw_num/dw_den
dw_statistic
```

# 3. Example 14.2 (p. 480-481)

## a) Update the dataset with additional information from Table 14.3 on p. 481.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df1$Population <- c(825000, 830445, 838750, 842940, 846315, 852240, 860760, 865925, 871640, 877745, 
                    886520, 894500, 900400, 904005, 908525, 912160, 917630, 922220, 925910, 929610)
```

## b) Model with the additional regressor; compare to Table 14.4 on p. 481.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod2 <- lm(Sales ~ Expenditures + Population, data = df1)
kable(xtable(summary(mod2) ))
kable(anova(mod2))
dwtest(Sales ~ Expenditures + Population, order.by = df1$Year, data = df1)
```

## c) Plot R-Studen residuals versus order of observations; compare to Figure 14.2 on p. 482.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
R_Student2 <- rstudent(mod2) # Use rstudent() versus calculating manually
plot(df1$Year, R_Student2, xlab = "Time Order (Year)", ylab = "Externally Studentized Residuals",
  main = "Time Series Plot of Residuals")
lines(df1$Year, R_Student2)
```

# 4. Example 14.3 (p. 483-485)
## a) Initially assume straight-line relationship; compare to Table 14.6 on p. 484.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(df3$Price, df3$MarketShare, xlab = "Selling Price per Pound", ylab = "Market Share",
  main = "Example 14.3 Scatterplot")

mod3 <- lm(MarketShare ~ Price, data = df3)
kable(xtable(summary(mod3)))
```

## b) Perform Durbin-Watson test automatically using dwtest(); compare to Table 14.6 on p. 484

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df3_dw <- dwtest(MarketShare ~ Price, data = df3)
kable(xtable(summary(df3_dw)))
df3_dw
```

## c) Estimate model parameters using Cochrane-Orcutt method. Note: the cochrane.orcutt() function in the orcutt package does not give the same results as the two-stage approach in the textbook.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
co_mod <- cochrane.orcutt(mod3)
kable(print.orcutt(co_mod))
```

## d) Calculate psi_hat using sum() command.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
psi_hat <- sum(mod3$residuals[1:length(df3$Time) -
  1] * mod3$residuals[2:length(df3$Time)])/sum(mod3$residuals^2)
psi_hat
```

## e) Create transformations on the predictor and the response.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
y_new <- df3$MarketShare[2:length(df3$Time)] - psi_hat *
  df3$MarketShare[1:length(df3$Time) - 1]
x_new <- df3$Price[2:length(df3$Time)] - psi_hat * df3$Price[1:length(df3$Time) - 1]

# Change to the incorrect value in textbook
x_new[1] <- 0.533 
kable(cbind(y_new,x_new))
```

## f) Run the new regression model and compare to Table 14.7 on p. 484. 
Note: There is a mistake in the data table in the textbook. If manually building the transformation, the first x' data point will be approximately 0.5528463.
The first value in Table 14.5 in the x' column is 0.533. Textbook models were run using the printed values and will be slightly off.
Recommendation: run models both ways, one correctly and the other with the incorrect value in order to reproduce the results in the textbook.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_new <- lm(y_new ~ x_new)
kable(xtable(summary(mod_new))) 
dw_new <- dwtest(y_new ~ x_new)
kable(xtable(summary(dw_new)))
dw_new
```


