---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 5 Practical Exercise"
footer: `r paste('Lesson 5 Practical Exercise')`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(xtable)
options(xtable.comment = FALSE, xtable.type="latex")
```

One or more models from the Lesson 4 practical exercise will be necessary to complete the following requirements. If you so desire, you may add this material to the end of your .Rmd file from Lesson 4.

## a) Read data from data-ex-3-1.xlsx using the read.xlsx() command.
```{r, echo=T}
df <- read.xlsx('../Practical 4/data-ex-3-1.xlsx', sheetIndex = 1)
```

## b) Give names to columns using names() command and attach to the dataframe using attach(). Output data to make sure it reads properly using print(xtable(\textit{dataname}))
```{r, echo=T}
names(df) <- c("Observation", "Time","Cases", "Distance")
attach(df)
```

## c) Output data structure and dimensions using the str() and dim() commands.
```{r, echo=T}
sprintf('The data structure is a %s', typeof(df) )
sprintf('The dimensions are %i by %i', dim(df)[1], dim(df)[2])
```

```{r, echo=T}
mod <- lm(Time~Cases+Distance, data=df)
print(xtable(summary(mod)))
```


# 2. Example 3.8 (p. 98) 
## Calculate 95% confidence intervals for the regression parameters.

```{r, echo=T}
N <- dim(df)[1]
X <- matrix(c(rep(1, N), df[, "Cases"], df[, "Distance"]), ncol = 3, byrow = FALSE)
beta <- diag(t(X) %*% X )
beta_hat <- c(2.3412, 1.6159, 0.0144)
std_error <- c(1.0967, 0.1707, 0.0036)
t_vals <- c(2.13, 9.46, 3.98)
low_betas <- beta_hat - t_vals * std_error
high_betas <- beta_hat + t_vals * std_error

print(low_betas)
print(high_betas)
```

# 3. Example 3.9 (p.99)
## Calculate confidence interval for mean response about some point $x_0$.

```{r, echo=T}
x_0 = data.frame(Cases=c(1),
                 Distance=c(1))
conf = 0.95
alpha = 1 - conf
df = dim(df)[1] - dim(df)[2]

lower_mr <- predict(mod, x_0) - ( qt(alpha/2, df) * var(Time) )
upper_mr <- predict(mod, x_0) + ( qt(alpha/2, df) * var(Time) )

print(lower_mr)
print(upper_mr)
```

# 4. Example 3.12 (p. 104)
## Create prediction interval on a new observation. Use same $x_0$.

```{r, echo=T}

```

# 5. Example 3.14 (p.115-116)
## Create a model with standardized regression coefficients. Scale using the scale() function

```{r, echo=T}

```
