\documentclass[a4paper,man,natbib]{apa6}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{setspace}

%% Images
% \usepackage{graphicx}
% 	\graphicspath{ {./images/} }
% 	\usepackage{caption}

% Minted
	\usepackage[cache=false]{minted}
	\usepackage{xcolor}
		\definecolor{light-gray}{gray}{0.97}
	\usemintedstyle{vs}

% Title
	\title{Intro to Computational Statistics: Homework 5}
	\shorttitle{HW04}
	\author{Author: Brandon Hosley}
	\affiliation{Instructor: Liang Kong, Ph.D}

%\abstract{}

\usepackage{pdfpages}

\begin{document}
\maketitle
\singlespacing

\emph{A researcher designed an experiment to study the effects of three factors (location, nitrogen, and water) to the yields of certain crop. For each one of the two locations (Trtc: c0 \& c1), he planted the corps in 48 plots. Then he applied one of the 12 combinations of treatments, four different rates of nitrogen application (Trta: a0, a1, a2, and a3) and three different level of watering (Trtb: b0, b1, and b2) to four randomly select plots. The results of yields are recorded in a MS Excel file (HW5.xlsx which is located at “Data Set” folder). In the file, the rate of nitrogen application (Trta) is stored in column A; the level of watering (Trtb) is stored in column B, the location (Trtc) is stored in column C, and the yields (Yeild1, Yield2, Yield3, \& Yield4) are stored I the column D, E, F, \& G.
\\ Write a SAS Program to answer the following questions.}
	
\subsection*{Q1: Import MS Excel file HW5.xlsx and write it as a SAS data set. }
% \inputminted[breaklines,bgcolor=light-gray]{sas}{./Snippets/DAT502-HW5-1.sas}
% \includepdf[pages=-]{./Snippets/SAS Output HW5-1.pdf}

\subsection*{Q2: Fit the data with a statistical model with all the main effects and interaction effects. }
% \inputminted[breaklines,bgcolor=light-gray]{sas}{./Snippets/DAT502-HW5-2.sas}
% \includepdf[pages=-]{./Snippets/SAS Output HW5-2.pdf}

\subsection*{Q3: Fit the data with a statistical model with all significant (\alpha=0.05) main effects and interaction effects. }
% \inputminted[breaklines,bgcolor=light-gray]{sas}{./Snippets/DAT502-HW5-3.sas}
% \includepdf[pages=-]{./Snippets/SAS Output HW5-3.pdf}

\subsection*{Q4: Based on the results of problem 3, using Scheffe multiple-comparison procedure with α=0.01 to perform a multiple comparison of the average yields for different rates of nitrogen application. Which rate(s) has (have) the lowest average yields? }
% \inputminted[breaklines,bgcolor=light-gray]{sas}{./Snippets/DAT502-HW5-4.sas}
% \includepdf[pages=-]{./Snippets/SAS Output HW5-4.pdf}

\subsection*{Q5: Based on the results of problem 3, using Duncan multiple-range test with α=0.1 to perform a multiple comparison of the average yields for different levels of watering. Which level(s) has (have) the highest average yield? }
% \inputminted[breaklines,bgcolor=light-gray]{sas}{./Snippets/DAT502-HW5-5.sas}
% \includepdf[pages=-]{./Snippets/SAS Output HW5-5.pdf}

\subsection*{Q6: Based on the results of problem 3, using Fisher’s LSD test with α=0.025 to perform a multiple comparison of the average yields for different locations. Which location has a higher average yields? }
% \inputminted[breaklines,bgcolor=light-gray]{sas}{./Snippets/DAT502-HW5-6.sas}
% \includepdf[pages=-]{./Snippets/SAS Output HW5-6.pdf}

\subsection*{Q7: Based on the results of problem 3, using Tukey studentized range test with α=0.025 to perform a multiple comparison of the average yields for different rates of nitrogen application. Which rate(s) has (have) the highest average yields? }
% \inputminted[breaklines,bgcolor=light-gray]{sas}{./Snippets/DAT502-HW5-7.sas}
% \includepdf[pages=-]{./Snippets/SAS Output HW5-7.pdf}

\subsection*{Q8: Based on the results of problem 3, using Performs Dunnett’s two-tailed t test with α=0.025 to perform a comparison of the average yields of the control rate (a0) with other rates of nitrogen application. Which rates of nitrogen application has a significantly different average yields with the control rate? }
% \inputminted[breaklines,bgcolor=light-gray]{sas}{./Snippets/DAT502-HW5-8.sas}
% \includepdf[pages=-]{./Snippets/SAS Output HW5-8.pdf}

\end{document}