---
output:
  pdf_document: default
  html_document: default
date: "2023-05-03"
author: 'Brandon Hosley'
---
---
title: "Lesson 12 Practical Exercise"
footer: `r paste('Lesson 12 Practical Exercise')`
date: "`r format(as.Date(c('2021/05/05')), '%d %B %Y')`"
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(printr)
library(xtable)
library(formatR)
library(nlme)
options(xtable.comment = FALSE, xtable.type="latex")
```

# Perform data housekeeping - upload data for Example 8.1; name columns, display to make sure it reads properly, etc. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df_8.1 <- read.xlsx('./data-ex-8-1.xlsx', sheetIndex = 1, colIndex = c(2,3,4))
names(df_8.1) <- c('Hours', 'RPM', 'Tool Type')
```

# 2. Example 8.1 (p.262-264) 
## a) Create scatterplot to look at the data - all points look the same

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(df_8.1)
scatterplot3d::scatterplot3d(df_8.1)
```

## b)  Create scatterplot - distinguish between Tool Type using points() command to make Tool Type A green and Tool Type B red.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(x=df_8.1$RPM, y=df_8.1$Hours, col=NULL)
points(y=df_8.1[df_8.1$`Tool Type`=='A',]$Hours, x=df_8.1[df_8.1$`Tool Type`=='A',]$RPM, col='green')  
points(y=df_8.1[df_8.1$`Tool Type`=='B',]$Hours, x=df_8.1[df_8.1$`Tool Type`=='B',]$RPM, col='red')  
```

## c) Define indicator variables for Tool Type and add to dataframe

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df_8.1['Tool B'] = with(df_8.1, ifelse(df_8.1$`Tool Type` == 'B',1, 0) )
```

## d) Create linear model; compare to Table 8.2 on p. 264

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_81_d <- lm(df_8.1$Hours ~ df_8.1$RPM + df_8.1$`Tool B`)
summary(mod_81_d)
anova(mod_81_d)
```

The coefficients are the same, but I am not seeing the exact method that they used to derive their first half summary statistics.

## e) Check model adequacy with residual plots

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(df_8.1$RPM, residuals(mod_81_d))
qqplot(df_8.1$RPM, residuals(mod_81_d))
```

# 3. Example 8.2 (p.267-268)
# Fit a model were ToolType is expected to influence both slope and intercept; compare the two models using the Partial F-test

## a) Add column to dataframe for Interaction

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df_8.1['x1x2'] <- df_8.1$RPM * df_8.1$`Tool B`
```

## b) Create full model; compare to p. 267

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_full <- lm(df_8.1$Hours ~ df_8.1$RPM + df_8.1$`Tool B` + df_8.1$x1x2)
summary(mod_full)
```

## c) Calculate SS and df for Regression and Residual for full model; compare to Table 8.3, p. 268

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
print(sum(anova(mod_full)[-4,2])) # SSR
print(sum(anova(mod_full)[,2])) # SS
```

## d) Test significance of interaction term using Partial F-test. Use alpha = 0.05 as the significance level; compare to values on p. 268

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
anova(mod_81_d, mod_full)
```

Because 0.1955 > 0.05 we fail to reject the null hypothesis.

## e) Test hypothesis that the regression lines for each tool type are identical; compare to p. 268

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_red_A <- lm(df_8.1[df_8.1$`Tool Type`=='A',]$Hours ~ df_8.1[df_8.1$`Tool Type`=='A',]$RPM)
mod_red_B <- lm(df_8.1[df_8.1$`Tool Type`=='B',]$Hours ~ df_8.1[df_8.1$`Tool Type`=='B',]$RPM)
summary(mod_red_A)
summary(mod_red_B)
```

