---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 15 Practical Exercise"
footer: `r paste('Lesson 15 Practical Exercise')`
date: "`r format(as.Date(c('2021/05/17')), '%d %B %Y')`"
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(printr)
library(xtable)
library(formatR)
library(lmSubsets)
library(leaps)
library(gtools)
library(car)
library(dplyr)
library(broom)
library(MuMIn)
library(kableExtra)
options(xtable.comment = FALSE, xtable.type="latex")
```

```{r, include=FALSE}
kable <- function(data, ...) {
  knitr::kable(data, ..., format = 'latex', booktabs = TRUE, digits = 5, align = 'c') %>% 
    kable_styling( latex_options =c("hold_position") )
}
```

# Perform data housekeeping - upload data for the Examples 10.1, 11.2, and 11.3; name columns, display to make sure it reads properly, etc. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df_1 <- read.xlsx('./data-ex-10-1.xlsx', sheetIndex = 1)
df_2 <- read.xlsx('./data-ex-11-2.xlsx', sheetIndex = 1)
df_3 <- read.xlsx('./data-ex-11-3.xlsx', sheetIndex = 1)
```

# 2. Example 11.1 (p. 374-375)
## a) Reproduce Table 11.1 on p. 375

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60), results='asis'}
model1 <- lm(y~ x1+x2, data = df_1)
model2 <- lm(y~ x1+x2+x4, data = df_1)
df_1$'Model 1' <- predict(model1)
df_1$'Model 2' <- predict(model2)
kable(df_1)
```

# 3. Example 11.2 (p. 375-377)
## a) Distinguish between original data and new data.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60), results='asis'}
names(df_2) <- c("Observation", "City", "Time", "Cases", "Distance")
df_old <- df_2[!complete.cases(df_2), ]
kable( df_old )
df_new <- df_2[complete.cases(df_2), ]
kable( df_new )
```

\newpage

## b) Create model using original data.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_old <- lm(Time~Cases+Distance, data=df_old)
kable(xtable(summary(mod_old)))
```

## c) Predict values in new dataset using original model.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
new_pred <- predict(mod_old, newdata = df_new)
kable(new_pred)
```

\newpage

## d) Reproduce Table 11.2 on p. 376.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
table <- data.frame(df_new$Observation,  df_new$City,  df_new$Cases, 
                    df_new$Distance, df_new$Time, new_pred, df_new$Time-new_pred)
names(table) <- c('Observation', 'City', 'Cases, $x_1$', 'Distances, $x_2$', 
                  'Observed \nTime, $y$', '$\\hat y$', '$y-\\hat y$')

kable(table, escape = FALSE, row.names = FALSE) %>% 
  add_header_above(c(" " = 5, "Least-Squares Fit" = 2)) %>% 
  add_header_above(c(" " = 1, '(1)'=1, '(2)'=1, '(3)'=1, '(4)'=1, '(5)'=1, '(6)'=1)) 
```

# 4. Example 11.3 (p. 380-385)
## a) Split data into Estimation and Prediction sets.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
names(df_3) <- c("Observation", "City", "Time", "Cases", "Distance", "Set")
df_3_split <- split(df_3, df_3$Set)
Est_set <- df_3_split[1]$E
Pred_set <- df_3_split[2]$P
```

## b) Create model using estimation set and compare to model using full set. Compare to Table 11.5 on p. 384.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_est <- lm(Time ~ Cases + Distance, data = Est_set)
kable(xtable(summary(mod_est))) 

mod_full <- lm(Time ~ Cases + Distance, data = df_3)
kable(xtable(summary(mod_full)))
```

## c) Reproduce Table 11.6 on p. 385.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
preds <- predict(mod_est, newdata = Pred_set)

table <- data.frame(Pred_set$Observation, Pred_set$Time, preds, Pred_set$Time-preds)
names(table) <- c('Observation, $i$', 'Observed, $y_i$', 'Predicted, $\\hat y$', 'Prediction Error, $e_i= y_i-\\hat y_i$')

kable(table, escape = FALSE, row.names = FALSE) %>% 
  add_header_above(c(" " = 2, "Least-Squares Fit" = 2)) %>% 
  add_header_above(c(" " = 1, '(1)'=1, '(2)'=1, '(3)'=1)) 
```
