---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 16 Practical Exercise"
footer: `r paste('Lesson 16 Practical Exercise')`
date: "`r format(as.Date(c('2021/05/19')), '%d %B %Y')`"
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
library(kableExtra)
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(printr)
library(xtable)
library(formatR)
library(lmSubsets)
library(leaps)
library(gtools)
library(car)
library(dplyr)
library(broom)
library(MuMIn)
options(xtable.comment = FALSE, xtable.type="latex")
```

```{r, include=FALSE}
kable <- function(data, ...) {
  knitr::kable(data, ..., format = 'latex', booktabs = TRUE, digits = 5, align = 'c') %>% 
    kable_styling( latex_options =c("hold_position") )
}
```

# 2. Example 13.1 (p. 426-427)
## a) Create data frame with problem data.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
Years <- c(5.8, 15, 21.5, 27.5, 33.5, 39.5, 46, 51.5)
Cases <- c(0, 1, 3, 8, 9, 8, 10, 5)
Miners <- c(98, 54, 43, 48, 51, 38, 28, 11)
Proportion <- Cases/Miners
df_13 <- data_frame(Years,Cases,Miners,Proportion)
kable(df_13)
```

## b) Perform logistic regression using glm(). Compare output to Table 13.2 on p. 427.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
outcomes <- cbind(df_13$Cases, df_13$Miners-df_13$Cases)
mod_logreg <- glm(outcomes ~ Years, data = df_13, family = binomial)
kable(xtable(summary(mod_logreg)))
kable(confint(mod_logreg))
```

# 3. Example 13.2 (p. 428)
## Calculate odds ratio for the regressor variable; compare to p. 428. 
```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
kable(exp(coef(mod_logreg)))
```

# 4.Example 13.3 (p. 434-436)
## Add a quadratic term to the model

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_logreg_quad <- glm(outcomes ~ Years + I(Years^2), data = df_13, family = binomial)
```

# 5. Example 13.4 (p. 437)
## Test each regression coefficient for significance automatically using the summary() command.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
kable(xtable(summary(mod_logreg_quad)))
```

# 6. Example 13.5 (p. 438) ###
## a) Calculate confidence intervals automatically using confint().

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
kable(confint(mod_logreg_quad))
```

## b) Calculate by hand using Equation (13.25).

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
Z <- qnorm(1 - 0.05/2)
sprintf('Upper bounds: %f', coef(mod_logreg_quad) + Z * sqrt(diag(vcov(mod_logreg_quad))) )
sprintf('Lower bounds: %f', coef(mod_logreg_quad) - Z * sqrt(diag(vcov(mod_logreg_quad))) )
```

# 7.Example 13.6 (p. 438)
## On the original model, calculate a 95% confidence interval on the odds ratio using Equation (13.26).

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
sprintf('Upper bounds: %f',  exp(coef(mod_logreg) + Z * sqrt(diag(vcov(mod_logreg)))) )
sprintf('Lower bounds: %f',  exp(coef(mod_logreg) - Z * sqrt(diag(vcov(mod_logreg)))) )
```

# 8.Example 13.7 (p. 439-440)
## Create a 95% confidence interval on the predicted probability of Years = 40. First do automatically (Parts a-b), then do by hand (Parts c-f).

## a) Calculate predicted probability using predict(); compare to p. 439.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
new_point <- data.frame(Years = 40)
predict(mod_logreg, new_point, type = "response")
```

## b) Calculate the predicted linear predictor using predict(); compare to p. 439.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
linear_predictor <- predict(mod_logreg, new_point)
linear_predictor
```

## c) Define vector for the new observation.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
x0 <- c(1, 40)
```

## d) Calculate the variance of the new observation. The function vcov() automatically calculates $(X^TVX)^{-1}$. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
Var_x0 <- t(x0) %*% vcov(mod_logreg) %*% x0
Var_x0
```

## e) Calculate CI on linear predictor using Equation (13.27).

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
x0_Lower <- linear_predictor - Z * sqrt(Var_x0)
x0_Lower

x0_Upper <- linear_predictor + Z * sqrt(Var_x0)
x0_Upper
```

## f) Convert to probabilities using Equation (13.28).

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
Lower_prob <- exp(x0_Lower)/(1 + exp(x0_Lower))
Lower_prob

Upper_prob <- exp(x0_Upper)/(1 + exp(x0_Upper))
Upper_prob
```
