---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 1 Practical Exercise"
footer: `r paste('Lesson 1 Practical Exercise')`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(xtable)
options(xtable.comment = FALSE, xtable.type="latex")
```

# 1. Preliminaries
## a) Read data from data-ex-2-1.xlsx using the read.xlsx() command.

```{r, echo=T}
df <- read.xlsx('./data-ex-2-1.xlsx', sheetIndex = 1)
```

## b) Give names to columns using names() command and attach to the dataframe using attach(). Output data to make sure it reads properly using print(xtable(\textit{dataname}))
```{r, echo=T}
names(df)
attach(df)
```

## c) Output data structure and dimensions using the str() and dim() commands.
```{r, echo=T}
sprintf('The data structure is a %s', typeof(df) )
sprintf('The dimensions are %i by %i', dim(df)[1], dim(df)[2])
```

