---
output:
  pdf_document: default
  html_document: default
---
---
title: "L2 Practical Exercise"
footer: `r paste('L2 Practical Exercise')`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(xtable)
options(xtable.comment = FALSE, xtable.type="latex")
```

## a) Read data from data-ex-2-1.xlsx using the read.xlsx() command.

```{r, echo=T}
df <- read.xlsx('../Practical 1/data-ex-2-1.xlsx', sheetIndex = 1)
```

## b) Give names to columns using names() command and attach to the dataframe using attach(). Output data to make sure it reads properly using print(xtable(\textit{dataname}))
```{r, echo=T}
names(df)
```

## c) Output data structure and dimensions using the str() and dim() commands.
```{r, echo=T}
sprintf('The data structure is a %s', typeof(df) )
sprintf('The dimensions are %i by %i', dim(df)[1], dim(df)[2])
```

# 2. Example 2.1 (p. 15-18)
## a) Create scatterplot using plot().
```{r, echo=T}
plot(df[2:3])
```

## b) Create linear model "by hand".
### (1) First, perform intermediary calculations - $S_{yy}$, $S_{xx}$, $S_{xy}$, $\bar{x}$, $\bar{y}$, N.
```{r, echo=T}
x_bar <- mean(df[,2])
y_bar <- mean(df[,3])
Sxx <- sum((df[,2]-x_bar)**2)
Syy <- sum((df[,3]-y_bar)**2)
Sxy <- sum(df[,3]*(df[,2]-x_bar))
sprintf('%a, %a, %a, %a, %a',x_bar, y_bar, Sxx, Sxy, Syy)
```

### (2) Determine estimates for slope and intercept.
```{r, echo=T}
B_1 <- Sxy/Sxx
B_0 <- y_bar - B_1*x_bar
sprintf('%a, %a',B_0, B_1)
```

## c) Create linear model using lm() command and display output using the summary() command.
```{r, echo=T}
mod <- lm(formula = df[,3]~df[,2], df)
summary(mod)
```

# 3. Example 2.2 (p.21-22)
## a) Obtain ANOVA table elements (by hand) - $SS_T$, $SS_R$, $SS_{Res}$.
```{r, echo=T}
SS_T <- sum(df[,3]**2-length(df)*(y_bar**2))
SS_R <- -B_1*Sxy
SS_Res <- SS_R - SS_T
```
## b) Define degrees of freedom (by hand).
```{r, echo=T}
DegFree = length(df[,1])-2
```

## c) Obtain residual degrees of freedom automatically using df.residual().
```{r, echo=T}
res <- df.residual(mod)
print(res)
```

## d) Obtain estimated error variance (MS_Residual).
```{r, echo=T}

```

## e)Obtain ANOVA table using aov() command or anova() command and display output.
```{r, echo=T}
A <- anova(mod)
print(A)
```

# 4. Example 2.3 (p.25)
## a) Test significance of slope parameter (by hand) using the qt() and pt() commands for critical value and p-value for the t-distribution.
```{r, echo=T}

```

# 5. Example 2.4 (p. 28) 
## a) Test for significance of Regression (F-test) at .01 significance level.

### (1) By hand:
```{r, echo=T}

```

### (2) Using anova command:
```{r, echo=T}

```