---
output:
  pdf_document: default
  html_document: default
---
---
title: "Solution to Lesson 2 Practical Exercise"
footer: `r paste('Solution to Lesson 2 Practical Exercise')`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('C:/Users/natha/OneDrive/Documents/R/scripts/R/setup.R')
shiny::includeCSS('C:/Users/natha/OneDrive/Documents/R/scripts/css/flat-slidy.css')
shiny::includeScript("C:/Users/natha/OneDrive/Documents/R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('C:/Users/natha/OneDrive/Documents/R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('C:/Users/natha/OneDrive/Documents/R/scripts','js','hideout.js'))
library(xlsx)
#library(xtable)
options(xtable.comment = FALSE, xtable.type="latex")
```

## a) Read data from data-ex-2-1.xlsx using the read.xlsx() command.

```{r, echo=T}
rp_data <- read.xlsx("C:/Users/natha/OneDrive/Documents/Teaching/OPER679/WI23/Practical Exercises/Examples/data-ex-2-1.xlsx", 
                     sheetIndex = 1, sheetName=NULL, rowIndex=NULL,
                     startRow=NULL, endRow=NULL, colIndex= NULL, as.data.frame=TRUE, 
                     header=TRUE, colClasses=NA, keepFormulas=FALSE,
                     encoding="unknown")
```

## b) Give names to columns using names() command and attach to the dataframe using attach(). Output data to make sure it reads properly.
```{r, echo=T}
names(rp_data) <- c("Observation", "ShearStrength","Age")
attach(rp_data)
print(xtable(rp_data), floating=F, justify='center')
```

## c) Output data structure and dimensions using the str() and dim() commands.
```{r, echo=T}
str(rp_data)
dim(rp_data)
```


# 2. Example 2.1 (p. 15-18)
## a) Create scatterplot using plot().
```{r, echo=T}
plot(rp_data[,3],rp_data[,2], xlab="Age", ylab="Shear Strength")
plot(Age, ShearStrength, xlab="Age", ylab="Shear Strength")
```

## b) Create linear model "by hand".
### (1) First, perform intermediary calculations - $S_{yy}$, $S_{xx}$, $S_{xy}$, $\bar{x}$, $\bar{y}$, N.
```{r, echo=T}
Syy = sum(rp_data[,2]^2)-sum(rp_data[,2])^2/dim(rp_data)[1] # This is the shortcut SST formula
Sxx = sum(rp_data[,3]^2)-sum(rp_data[,3])^2/dim(rp_data)[1] # Same thing, just for independent variable
Sxy = sum(rp_data[,2]*rp_data[,3]) - (sum(rp_data[,2])*sum(rp_data[,3]))/dim(rp_data)[1]
x_bar = mean(rp_data[,3])
y_bar = mean(rp_data[,2])
N = dim(rp_data)[1]
```

We have: $S_{yy}$ = `r Syy`, $S_{xx}$ = `r Sxx`, $S_{xy}$ = `r Sxy`, $\bar{x}$ = `r x_bar`,
$\bar{y}$ = `r y_bar` and $N$ = `r N`.

### (2) Determine estimates for slope and intercept.
```{r, echo=T}
SlopeEstimate = Sxy/Sxx
InterceptEstimate = y_bar - SlopeEstimate*x_bar
```

We have $\beta_0$ = `r InterceptEstimate`

## c) Create linear model using lm() command and display output using the summary() command.
```{r, echo=T}
rp_model <- lm(ShearStrength ~ Age)
print(xtable(summary(rp_model)))
```

# 3. Example 2.2 (p.21-22)
## a) Obtain ANOVA table elements (by hand) - $SS_T$, $SS_R$, $SS_{Res}$.
```{r, echo=T}
SST = Syy # Calculated above
SS_Regression = SlopeEstimate*Sxy
SS_Residual = SST - SlopeEstimate*Sxy
```
## b) Define degrees of freedom (by hand).
```{r, echo=T}
dfT = N - 1
df_Regression = 1 # Equal to number of regressors
df_Residual = dfT - df_Regression
```

## c) Obtain residual degrees of freedom automatically using df.residual().
```{r, echo=T}
print(df.residual(rp_model))

```

## d) Obtain estimated error variance (MS_Residual).
```{r, echo=T}
VarianceEstimate = SS_Residual / df_Residual
print(VarianceEstimate)
```

## e)Obtain ANOVA table using aov() command or anova() command and display output.
```{r, echo=T}
aov.out <- aov(ShearStrength~Age, data=rp_data)
print(xtable(summary(aov.out)))

print(xtable(anova(rp_model)))
```

# 4. Example 2.3 (p.25)
## a) Test significance of slope parameter (by hand) using the qt() and pt() commands for critical value and p-value for the t-distribution.
```{r, echo=T}
significanceLevel = 0.05
significanceLevel
standardError_SlopeEstimate = sqrt(VarianceEstimate / Sxx)
standardError_SlopeEstimate
testStatistic = SlopeEstimate / standardError_SlopeEstimate
testStatistic
t_critical = qt(1 - significanceLevel/2, df_Residual)
t_critical
p_val = 2*pt(testStatistic, df_Residual)
p_val
```

# 5. Example 2.4 (p. 28) 
## a) Test for significance of Regression (F-test) at .01 significance level.

### (1) By hand:
```{r, echo=T}
significanceLevel = 0.01
F_testStatistic = (SS_Regression / df_Regression) / VarianceEstimate
F_testStatistic
F_critical = qf(1-significanceLevel, df_Regression, df_Residual)
F_critical
p_val = 1 - pf(F_testStatistic, df_Regression, df_Residual)
p_val
```

### (2) Using anova command:
```{r, echo=T}
print(xtable(anova(rp_model)))
```

Observing the F-statistic of `r F_testStatistic` and the small p-value of `r p_val`, we can conclude that there is significant evidence that the slope parameter is not equal to zero.