---
title: "Homework 1"
output: pdf_document
date: "2023-04-05"
---
---
title: "Homework 1"
footer: `HW 1`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

```{r setup, include=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(xtable)
options(xtable.comment = FALSE, xtable.type="latex")
```

## Problem 1.

Analyze the relationship between a team’s offensive capabilities ($x_1$ and $x_2$) and total team
wins ($y$).

```{r, echo=TRUE}
df <- read.xlsx('./1989 NFL Season Data (Handout).xlsx', sheetIndex = 1)
attach(df)
```

### (a)

 Create two simple linear regression models, one using $x_1$ as the independent variable and the other
using $x_2$. The dependent variable is games won ($y$). Report the estimated regression equation for each
model and test each model for significance of the slope parameter. The hypothesis test should contain
your test statistic, critical value, p-value, decision, and conclusion (in the context of the problem).

```{r, echo=TRUE}
mod_1 <- lm(y ~ x1)
mod_2 <- lm(y ~ x2)
```

### (b)

### (c)

### (d)

### (e)

## Problem 2.

### (a)

### (b)

### (c)

### (d)