\chapter{Introduction}
\label{ch:introduction}
\glsresetall

This final project is designed to showcase the understanding and application of the concepts and methodologies taught in the OPER 679 course. The project will employ a variety of techniques, some of which may not be the most optimal for the given scenario. However, these suboptimal techniques are included intentionally to demonstrate their application and potential outcomes. Each technique's usage and context will be thoroughly discussed when they are implemented.

The project's focus will be on a dataset sourced from fantasy football statistics. This dataset will serve as the basis for our exploration and application of the course material, providing a practical and engaging context for demonstrating competency in the course objectives.

Fantasy football has grown exponentially over the past decade, with millions of people participating worldwide. The game involves drafting real-world football players to form a virtual team, with points awarded based on the players' actual performance in games. A key challenge for participants is predicting player performance in the upcoming season, which is crucial for successful drafting and team management.

The use of statistical modeling techniques to predict player performance in fantasy football is not a new concept. Various studies have attempted to apply different predictive models to this problem, with varying degrees of success. Linear regression, in particular, has been a popular choice due to its simplicity, interpretability, and effectiveness in capturing relationships between variables.



