---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 7 Practical Exercise"
footer: `r paste('Lesson 7 Practical Exercise')`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(printr)
library(xtable)
library(formatR)
library(ggplot2)
library(psych)
options(xtable.comment = FALSE, xtable.type="latex")
options(rgl.useNULL=TRUE)
#.rs.restartR()
library(qpcR)
```

# Perform data housekeeping - upload data for Example 5.1 and Example 5.2, name columns, display to make sure it reads properly, etc. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df <- read.xlsx('./data-ex-5-1.xlsx', sheetIndex = 1)
names(df) <- c('Customer', 'x (kWh)', 'y (kW)')
```

# 2. Example 5.1 (p. 173-175)

## a) Create scatterplot of data

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(x=df$`x (kWh)` , y=df$`y (kW)`)
```

## b) Create linear model and display ANOVA table. Compare to least squares fit on p. 173 and ANOVA table on p. 175

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod <- lm(df$`y (kW)`~df$`x (kWh)`)
summary(mod)
anova(mod)
```

## c) Create plot of R-Student values versus fitted values

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(resid(mod))
```

## d) Transform and regress on y* = sqrt(y).Compare to least squares fit on p. 173

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_root <- lm(sqrt(df$`y (kW)`)~df$`x (kWh)`)
summary(mod_root)
anova(mod_root)
```

## e) Create plot of R-Student values versus fitted values of transformed model

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(resid(mod_root))
```

# 3. Example 5.3 (p. 184)

## a) Perform Box-Cox transformation of Electric Utility data using boxcox() function

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
bc <- boxcox(df$`y (kW)`~df$`x (kWh)`)
```

## b) The boxcox() function outputs a range of x and y values. Plot those values and compare to p. 185. Why are the plots different?

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(bc)
```

Page 185 show residuals, whereas the plot above is a plot of the transformed values without a new regression.

## c) Find value of lambda ("y" in R's boxcox notation) using which() and max() functions

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
lambda <- bc$x[which.max(bc$y)]
```

## d) Transform y (Demand) using Box-Cox transformation Equation 5.1 on p. 182. Vary lambda values and compare SS_Residual to Table 5.7 on p. 185

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_bc <- lm(((df$`y (kW)`^lambda-1)/lambda) ~ df$`x (kWh)`)
plot(resid(mod_bc))
```

# 4. Example 5.2 (p. 178-181)

## a) Create scatterplot to visualize data

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df2 <- read.xlsx('./data-ex-5-2.xlsx', sheetIndex = 1)
names(df2) <- c('Observation', 'Wind', 'Output')
plot(df2$Wind, df2$Output)
```

## b) Fit linear model first; compare results to p. 178

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod2 <- lm(df2$Output~df2$Wind)
summary(mod2)
anova(mod2)
```

## c) Create residual plots - R-Student and raw residuals versus fitted values

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(resid(mod2))
```

## d) Residual plots show clear nonlinearity. Attempt to rectify through transformation: x' = 1/x

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod_inv <- lm(df2$Output ~ 1/df2$Wind)
```

## e) Create scatterplot and model using transformed data; compare to p. 180 and 181

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
ggplot(df2, aes(1/df2$Wind, df2$Output)) +
  geom_point() +
  geom_smooth(method='lm', se=FALSE) 
```

Appears to be essentially the same as the graph on page 181.

## f) Plot residuals versus fitted values; compare to p. 182

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(resid(mod_inv))
```

# 5. Example 5.4 (p. 187)

## Determine alpha value to transform independent variable using Box-Tidwell Procedure

### Step 1.0: Define alpha_0 = 1 and run simple regression model (performed in Example 5.2 above)

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
alpha_0 <- 1
mod_bt <- lm(df2$Output ~ df2$Wind)
summary(mod_bt)
```

### Step 1.1: Define w = x ln x and add to model as an independent variable; compare output to p. 187

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df2['w'] <- df2$Wind * log(df2$Wind)
mod_bt2 <- lm(df2$Output ~ df2$Wind + df2$w)
summary(mod_bt2)
```

### Step 1.2: Using  Equation 5.10, calculate alpha_1; compare to p. 187 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
alpha_1 = -0.46260/0.24115 + 1
alpha_1
```

### Step 2.0: Define x' = x^alpha_1 and regress model with alpha_0 = 0; compare to p. 187

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df2["x_p"] <- df2$Wind**alpha_1
mod_bt3 <- lm(df2$Output ~ df2$x_p)
summary(mod_bt3)
```

### Step 2.1: Define w' = x' ln x', add as independent variable, and run model

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df2['w_p'] <- df2$x_p * log(df2$x_p)
mod_bt4 <- lm(df2$Output ~ df2$x_p + df2$w_p)
summary(mod_bt4)
```

### Step 2.2: Using equation 5.10, calculate alpha_2; compare to value on p. 187. Pretty close to -1, which was the transformation in Example 5.2. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
alpha_2  =  0.5995 /  -6.67844 + alpha_1
alpha_2
```

Very close to the textbook answer.