---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 9 Practical Exercise"
footer: `r paste('Lesson 9 Practical Exercise')`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(printr)
library(xtable)
library(formatR)
library(nlme)
library(MASS)
options(xtable.comment = FALSE, xtable.type="latex")
```

# Perform data housekeeping - upload data for the Delivery Time example (we will use Example 5.7); name columns, display to make sure it reads properly, etc. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df <- read.xlsx('./data-ex-5-7.xlsx', sheetIndex = 1)
names(df) <- c('observation', 'time', 'cases', 'distance', 'city')
df
```

# 2. Example 6.1 (p.213-214) 
## a) Calculate hat matrix values

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
N <- dim(df)[1]
X <- matrix(c(df$cases, df$distance, rep(1, N)), ncol = 3, byrow = FALSE)
H <- X%*%ginv(t(X)%*%X)%*%t(X)
diag(H)
```

## b) Create data frame to reproduce Table 6.1 on p. 214 - start with column for Observation and $h_{ii}$

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
table_6_1 <- data.frame(df$observation)
table_6_1['h_ii'] <- diag(H)
mod <- lm(df$time~df$cases+df$distance)
```

## c) Create shell of unnamed table on p. 213

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
unnamed <- data.frame(Run = c('9 and 22 in', '9 out', '22 out', '9 and 22 out'))
```

## d) Create models for the four scenarios in the unnamed table on p. 213. Note: Deletions using subset= are done sequentially. So, subset=(1:N)[-1][-2] removes the first observation and then the second of the remaining observations.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod1 <- lm(df$time ~ df$cases + df$distance)
mod2 <- lm(df[c(-9),]$time ~ df[c(-9),]$cases + df[c(-9),]$distance)
mod3 <- lm(df[c(-22),]$time ~ df[c(-22),]$cases + df[c(-22),]$distance)
mod4 <- lm(df[c(-9,-22),]$time ~ df[c(-9,-22),]$cases + df[c(-9,-22),]$distance)

unnamed['BetaHat0'] <- c(coef(mod1)[1], coef(mod2)[1], coef(mod3)[1], coef(mod4)[1])
unnamed['BetaHat1'] <- c(coef(mod1)[2], coef(mod2)[2], coef(mod3)[2], coef(mod4)[2])
unnamed['BetaHat2'] <- c(coef(mod1)[3], coef(mod2)[3], coef(mod3)[3], coef(mod4)[3])
unnamed['MS_Res'] <- c(anova(mod1)[3,3], anova(mod2)[3,3], anova(mod3)[3,3], anova(mod4)[3,3])
unnamed['R2'] = c(summary(mod1)$r.squared, summary(mod2)$r.squared, summary(mod3)$r.squared, summary(mod4)$r.squared)
```

## e)Display completed (unnamed) table on bottom of p. 213

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
unnamed
```

# 3. Example 6.2 (p.216)

## a) Calculate Cook's D using Equation 6.5

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
((rstudent(mod)^2)/2)*(table_6_1$h_ii/(1-table_6_1$h_ii))

```

## b) Calculate Cook's D using cooks.distance(). Does this give the same answer as the "by hand" approach?

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
cooks.distance(mod)
```

## c) Add Cook's D to the Table 6.1 dataframe

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
table_6_1['D_i'] <- cooks.distance(mod)
```

# 4. Example 6.3 (p.218-219)

## a) Calculate DFFITS and DFBETAS using R

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
R <- ginv(t(X)%*%X)%*%t(X)
DFFITS <- sqrt(table_6_1$h_ii/(1-table_6_1$h_ii))*rstudent(mod)
DFBETAS <- dfbetas(mod)
colnames(DFBETAS) <- c('Intercept DFBETAS','Cases DFBETAS','Distance DFBETAS')
```

## b) Update Table 6.1

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
table_6_1['DFFITS'] <- DFFITS
table_6_1 <- cbind(table_6_1, DFBETAS)
```

# 5. Example 6.4 (p. 219)

## a) Calculate Covariance Ratio using R

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
CR <- covratio(mod)
```

## b) Update Table 6.1

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
table_6_1['COVRATIO'] <- CR
table_6_1
```

## c) Identify observations that exceed limits of $1 \pm 3\frac{p}{n}$ for COVRATIO using which() and the "or" logical operator (|). Are these the same points identified in the textbook?

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
which(table_6_1$COVRATIO > (1+(9/25)) | table_6_1$COVRATIO < (1-(9/25)))
```

The same, but with the addition of entry 16.
