\documentclass[a4paper,man,natbib]{apa6}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{setspace}

%% Images
% \usepackage{graphicx}
% 	\graphicspath{ {./images/} }
% 	\usepackage{caption}

% Minted
	\usepackage[cache=false]{minted}
	\usepackage{xcolor}
		\definecolor{light-gray}{gray}{0.97}
	\usemintedstyle{vs}

% Title
	\title{Intro to Computational Statistics: Homework 2}
	\shorttitle{HW01}
	\author{Author: Brandon Hosley}
	\affiliation{Instructor: Liang Kong, Ph.D}

%\abstract{}

\begin{document}
\maketitle
\singlespacing
	
\subsection*{Q1:}
\emph{Write a SAS program to list the data from SAS data set: students.sas7bdat to fulfill the following requirements:}
\begin{itemize}
	\itemsep-0.5em
	\item Double space.
	\item A separate listing for different major.
	\item With the number of observations and the total teaching efficiency for each major at the end of each page. 
\end{itemize}
	\inputminted[bgcolor=light-gray]{sas}{./Snippets/DAT502-HW2-1.sas}

\subsection*{Q2:}
\emph{Write a SAS program to describe the data from SAS data set: students.sas7bdat by:}
\begin{itemize}
	\itemsep-0.5em
	\item A vertical histogram of Major and each bar is verified by the Gender.
	\item A pie chart of Final Grade which show the relative frequency only
	\item A horizontal histogram of final examination's score with midpoints as 45, 50, 55,....,95.
	\item A block chart with the high of each block represent the average of IQ for each major and gender.
	\item A star chart of grade.
\end{itemize}
	\inputminted[bgcolor=light-gray]{sas}{./Snippets/DAT502-HW2-2.sas}

\subsection*{Q3:}
\emph{Write a SAS program to draw a simple linear regression line and 90\% predicted interval to fit teaching efficiency as dependent variable and the score of Math part of SAT as independent variable for the data from SAS data set: students.sas7bdat. }
	\inputminted[bgcolor=light-gray]{sas}{./Snippets/DAT502-HW2-3.sas}

\subsection*{Q4:}
\emph{Write a SAS program to draw a three-dimensional scatter graph of the score Math part of SAT (as y-variable), the score of IQ (as x-variable), and teaching efficiency (as z-variable).}
	\inputminted[bgcolor=light-gray]{sas}{./Snippets/DAT502-HW2-4.sas}
	
\end{document}
	\inputminted[bgcolor=light-gray]{sas}{./Snippets/DAT502-HW1.sas}