---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 17 Practical Exercise"
footer: `r paste('Lesson 17 Practical Exercise')`
date: "`r format(as.Date(c('2021/05/24')), '%d %B %Y')`"
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
library(kableExtra)
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(readxl)
library(printr)
library(xtable)
library(formatR)
library(boot)
options(xtable.comment = FALSE, xtable.type="latex")
```

```{r, include=FALSE}
kable <- function(data, ...) {
  knitr::kable(data, ..., format = 'latex', booktabs = TRUE, digits = 5, align = 'c') %>% 
    kable_styling( latex_options =c("hold_position") )
}
```

# Perform data housekeeping - upload data for Resistivity Example, name columns, display to make sure it reads properly, etc. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df <- read_excel('./Resistivity Example.xlsx')
```

# 2. Resistivity Example (p. 60-65 in Video lecture notes)
## a) Add columns to the data frame for interactions (2-way, 3-way, 4-way) 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
attach(df)

df$x12 <- x1 * x2
df$x123 <- x1 * x2 * x3
df$x124 <- x1 * x2 * x4
df$x1234 <- x1 * x2 * x3 * x4

df$x13 <- x1 * x3
df$x134 <- x1 * x3 * x4

df$x14 <- x1 * x4

df$x23 <- x2 * x3
df$x234 <- x2 * x3 * x4

df$x24 <- x2 * x4
df$x34 <- x3 * x4
detach(df)
```

## b) Model using glm(), family = Gamma, link = log.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod <- glm(y~.,df, family = Gamma(link = 'log'))
kable(xtable(mod))
```

## c) Model using main effects and two-way interactions

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mod2 <- glm(y ~ x1 + x2 + x3 + x4 + x13 + x23 + x34, family = Gamma(link = "log"), data = df)
kable(xtable(mod2))
glm.diag.plots(mod2)
```

