---
output:
  pdf_document: default
  html_document: default
---
---
title: "Lesson 14 Practical Exercise"
footer: `r paste('Lesson 14 Practical Exercise')`
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(printr)
library(xtable)
library(formatR)
library(lmSubsets)
library(leaps)
library(gtools)
library(car)
library(dplyr)
library(broom)
library(MuMIn)
library(kableExtra)
library(stringr)
options(xtable.comment = FALSE, xtable.type="latex")
options(rgl.useNULL=TRUE)
#.rs.restartR()
library(qpcR)
```

```{r, include=FALSE}
kable <- function(data, ...) {
  knitr::kable(data, ..., 'latex', booktabs = TRUE, digits = 5, align = 'c') %>% 
    kable_styling( latex_options =c("hold_position"))
}
```

# Perform data housekeeping - upload data for the Jet Turbine example; name columns, display to make sure it reads properly, etc. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df_B13 <- read.xlsx('./data-table-B13.xlsx', sheetIndex = 1)
names(df_B13) = c("thrust", "primary", "secondary", "fuel", "press", "exhaust", "ambient")
```

# 2. Jet Turbine Example
## a) Use dredge() function to automatically perform all regressors regression

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
lmod <- lm(thrust~., data = df_B13, na.action = "na.fail")
kable(summary(dredge(lmod))) %>% kable_styling( latex_options =c("hold_position","scale_down") )
```

Unfortunately the output of Dredge is not very conducive to manipulation for table setting.

## b) Analyze Model A (p. 15 in Vining Lecture Video notes). Reproduce the results shown in pages 16-20.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
modelA <- lm(thrust ~ primary + fuel + exhaust + ambient, data=df_B13)
print((summary(modelA)))
kable(anova(modelA))
print(vif(modelA))

#residuals_A <- residuals(modelA)
press_A <- PRESS(modelA)
domain <- c(1:length(press_A$residuals))
sprintf("PRESS = %f", press_A$stat)
sprintf("R-Sq(pred) = %f", press_A$P.square)
qqnorm(press_A$residuals, main = "Normal Probability Plot")

plot(predict(modelA), press_A$residuals, ylab = "Deleted Residual",
xlab = "Fitted Value", main = "Versus Fits")

plot(domain, press_A$residuals, type = "b", pch = 19,
col = "blue", xlab = "Observation Order", ylab = "Deleted Residual")

plot(df_B13$primary, press_A$residuals, ylab = "Deleted Residual", xlab = "primary",
main = "Residuals versus primary")

plot(df_B13$fuel, press_A$residuals, ylab = "Deleted Residual", xlab = "fuel",
main = "Residuals versus fuel")

plot(df_B13$exhaust, press_A$residuals, ylab = "Deleted Residual", xlab = "exhaust",
main = "Residuals versus exhaust")

plot(df_B13$ambient, press_A$residuals, ylab = "Deleted Residual", xlab = "ambient",
main = "Residuals versus ambient")
```

## c) Analyze Model B (p. 15 in Vining Lecture Video notes). Reproduce the results shown in pages 21-26.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
modelB <- lm(thrust ~ primary + fuel + exhaust + ambient + press, data=df_B13)
print((summary(modelB)))
kable(anova(modelB))
print(vif(modelB))

press_B <- PRESS(modelB)
domain <- c(1:length(press_B$residuals))
sprintf("PRESS = %f", press_B$stat)
sprintf("R-Sq(pred) = %f", press_B$P.square)
qqnorm(press_B$residuals, main = "Normal Probability Plot")

plot(predict(modelB), press_B$residuals, ylab = "Deleted Residual",
xlab = "Fitted Value", main = "Versus Fits")

plot(domain, press_B$residuals, type = "b", pch = 19,
col = "blue", xlab = "Observation Order", ylab = "Deleted Residual")

plot(df_B13$primary, press_B$residuals, ylab = "Deleted Residual", xlab = "primary",
main = "Residuals versus primary")

plot(df_B13$fuel, press_B$residuals, ylab = "Deleted Residual", xlab = "fuel",
main = "Residuals versus fuel")

plot(df_B13$press, press_B$residuals, ylab = "Deleted Residual", xlab = "press",
main = "Residuals versus press")

plot(df_B13$exhaust, press_B$residuals, ylab = "Deleted Residual", xlab = "exhaust",
main = "Residuals versus exhaust")

plot(df_B13$ambient, press_B$residuals, ylab = "Deleted Residual", xlab = "ambient",
main = "Residuals versus ambient")
```

## d) Analyze Model C (p. 15 in Vining Lecture Video notes). Reproduce the results shown in pages 27-32.

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
modelC <- lm(thrust ~ primary + exhaust + ambient + press, data=df_B13)
print((summary(modelC)))
kable(anova(modelC))
print(vif(modelC))

press_C <- PRESS(modelC)
domain <- c(1:length(press_C$residuals))
sprintf("PRESS = %f", press_C$stat)
sprintf("R-Sq(pred) = %f", press_C$P.square)
qqnorm(press_C$residuals, main = "Normal Probability Plot")

plot(predict(modelC), press_C$residuals, ylab = "Deleted Residual",
xlab = "Fitted Value", main = "Versus Fits")

plot(domain, press_C$residuals, type = "b", pch = 19,
col = "blue", xlab = "Observation Order", ylab = "Deleted Residual")

plot(df_B13$primary, press_C$residuals, ylab = "Deleted Residual", xlab = "primary",
main = "Residuals versus primary")

plot(df_B13$press, press_C$residuals, ylab = "Deleted Residual", xlab = "press",
main = "Residuals versus press")

plot(df_B13$exhaust, press_C$residuals, ylab = "Deleted Residual", xlab = "exhaust",
main = "Residuals versus exhaust")

plot(df_B13$ambient, press_C$residuals, ylab = "Deleted Residual", xlab = "ambient",
main = "Residuals versus ambient")
```
