\documentclass[12pt,letterpaper]{exam}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[width=8.50in, height=11.00in, left=0.50in, right=0.50in, top=0.50in, bottom=0.50in]{geometry}

\usepackage{libertine}
\usepackage{multicol}
\usepackage[shortlabels]{enumitem}

\usepackage{booktabs}
\usepackage[table]{xcolor}

\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{bbm}

\usepackage{hyperref}
\usepackage{graphicx}
%\usepackage{wrapfig}
%\usepackage{capt-of}
%\usepackage{tikz}
%\usepackage{pgfplots}
%\usetikzlibrary{shapes,arrows,positioning,patterns}
%\usepackage{pythonhighlight}

%\newcommand\chapter{}
%\renewcommand{\thequestion}{\textbf{\chapter.\arabic{question}}}
%\renewcommand{\questionlabel}{\thequestion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\class}{EENG 645} % This is the name of the course 
\newcommand{\assignmentname}{Final Project Dataset} % 
\newcommand{\authorname}{Hosley, Brandon} % 
\newcommand{\workdate}{\today} % 
\printanswers % this includes the solutions sections
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}
\pagestyle{plain}
\thispagestyle{empty}
\noindent
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r @{\extracolsep{10pt}} l}
	\textbf{\class} & \textbf{\authorname}  &\\ %Your name here instead, obviously 
	\textbf{\assignmentname } & \textbf{\workdate} & \\
\end{tabular*}\\ 
\rule{\textwidth}{2pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HEADER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}
	\question 
	What is your topic area?
	\begin{solution}
		I am studying reinforcement learning and utilizing the Starcraft2 Learning Environment.
	\end{solution}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\question 
	What are the inputs and outputs for your problem?
	\begin{solution}
		For initial training there are a series of playbacks of games including the outcome of the game. \\
		For the training portion of the research the outputs will also include updates to the agents that have played
		a round of the game.
	\end{solution}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\question 
	How will you get data for your project?
	\begin{solution}
		The playback data has been graciously provided by Blizzard and Deepmind.
	\end{solution}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\question 
	If collecting your own data, is it feasible you will actually get enough data in the next few weeks to complete the project? 
	\begin{solution}
		Initial training data is collected. I do not believe any of the self and league play data will be available in a reasonable time.
	\end{solution}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\question 
	If utilizing an existing dataset, are you sure the dataset contain everything you need (is it a labeled) dataset?
	\begin{solution}
		It is labeled for its purpose.
	\end{solution}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\question 
	If simulating, what are your methods to create synthetic data? 
	It is high-enough fidelity to actually be worth pursuing? 
	Do you have a path forward (someone else’s simulation code?) or do you need to write your own simulation software?
	\begin{solution}
		The available data is enough to provide initial training for others who have built networks using the same environment.
	\end{solution}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\question 
	What is the ANN architecture (Dense, CNN, RNN, 1D ConvNet, etc.)?
	\begin{solution}
		The architecture consists of more than one network, but all of them are Deep networks or RNNs.
	\end{solution}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\question 
	What will your baseline to compare against be (also include possible metrics)?
	\begin{solution}
		Effectiveness is typically based on the model's win-rate against some set of opponents.
		I intend to base it on win rate against built in Computer Players, divided by their assigned difficulty; easy, medium, hard, etc.
	\end{solution}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\question 
	Are you all set to go from a hardware point of view?
	\begin{solution}
		I am currently working with my advisor to implement the simulations within the ANT Center
	\end{solution}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{questions}
\end{document}
