---
output:
  pdf_document: default
  html_document: default
date: "2023-05-01"
author: 'Brandon Hosley'
---
---
title: "Lesson 11 Practical Exercise"
footer: `r paste('Lesson 11 Practical Exercise')`
date: "`r format(as.Date(c('2021/05/03')), '%d %B %Y')`"
output:
  pdf_document:
    df_print: kable
  html_document:
    df_print: paged
  slidy_presentation:
    code_folding: hide
    fig_caption: yes
    smart: no
keep_tex: yes
graphics: yes
---

# 1. Preliminaries

```{r intro, echo=FALSE,message=FALSE, warning=FALSE}
source('../R/scripts/R/setup.R')
shiny::includeCSS('../R/scripts/css/flat-slidy.css')
shiny::includeScript("../R/scripts/js/jquery.min.js")
shiny::includeScript(system.file('../R/scripts','js','tpt-scroll.js'))
shiny::includeScript(system.file('../R/scripts','js','hideout.js'))
library(xlsx)
library(printr)
library(xtable)
library(formatR)
library(nlme)
options(xtable.comment = FALSE, xtable.type="latex")
```

# Perform data housekeeping - upload data for Example 7.1 and Example 7.2; name columns, display to make sure it reads properly, etc. 

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df_7.1 <- read.xlsx('./data-ex-7-1.xlsx', sheetIndex = 1)
names(df_7.1) <- c('Hardwood Concentration', 'Tensile Strength (psi)')

df_7.2 <- read.xlsx('./data-ex-7-2.xlsx', sheetIndex = 1)
names(df_7.2) <- c('Observation', 'Time (s)', 'Voltage Drop')
```

# 2. Example 7.1 (p.227-229) 
## a) Create scatterplot

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(df_7.1$`Hardwood Concentration`, df_7.1$`Tensile Strength (psi)`)
```

## b) Fit a quadratic model on centered data; compare to p. 227

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
df_7.1$hw_con2 <- df_7.1$`Hardwood Concentration`**2
qmod_7.1 <- lm(df_7.1$`Tensile Strength (psi)` ~ 
                 df_7.1$`Hardwood Concentration` + df_7.1$hw_con2)
summary(qmod_7.1)

vals <- seq(0, 14, 0.2)
preds_7.1 <- predict(qmod_7.1, list(vals))

plot(df_7.1$`Hardwood Concentration`, df_7.1$`Tensile Strength (psi)`)
lines(df_7.1$`Hardwood Concentration`, preds_7.1)
```

## c) Create ANOVA table (by hand and with R); compare to Table 7.2 on p. 228

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
anova(qmod_7.1)
```

## d) Test significance of quadradic term using Partial F-test. Use alpha = 0.01 as the significance level. Compare to p. 229

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
qmod_7.1_partial <- lm(df_7.1$`Tensile Strength (psi)` ~ df_7.1$hw_con2)
anova(qmod_7.1_partial)
```
```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
(415.07-312.64)/(17-16)/(312.64/1)
```



## e) Create residuals versus fits plot

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(df_7.1$`Hardwood Concentration`, residuals(qmod_7.1))
```

## f) Create normal probability plot of residuals

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
qqplot(df_7.1$`Hardwood Concentration`, residuals(qmod_7.1))
```

# 3. Example 7.2 (p.231-234)

## a) Create scatterplot

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
plot(df_7.2$`Time (s)`, df_7.2$`Voltage Drop`)
```

## b) Fit a cubic spline using two knots, one at  $t_1$ = 6.5 and one at $t_2$ = 13

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
library(splines)
csmod_7.2 <- lm(df_7.2$`Voltage Drop` ~ ns(df_7.2$`Time (s)`, knots = c(6.5,13)) )
summary(csmod_7.2)

vals <- seq(0, 21, 0.2)
preds_7.2 <- predict(csmod_7.2, list(vals))

plot(df_7.2$`Time (s)`, df_7.2$`Voltage Drop`)
lines(df_7.2$`Time (s)`, preds_7.2)
```

## c) Create indicator functions for the two knots

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}

```

## d) Add columns to dataframe for the higher-order terms and spline terms

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}

```

## e) Fit model; compare to values in Table 7.4, p. 233

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}

```

## f) Reproduce ANOVA table on p. 233

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}

```

## g) Test significance of spline terms using Partial F-test. Use alpha = 0.01 as the significance level

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}

```

## h) Create residuals versus fits plot for each model

```{r, echo=T, tidy=TRUE, tidy.opts=list(width.cutoff=60)}

```
